---
title: "Table 1"
author: "Gerko Vink"
date: Characteristics of respondents by background variables and by the 10 explanatory
  variable scales
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(tibble)   # Tibbles
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
```

---

# Field $\times$ Rank
```{r}
d50[[1]] %$% table(Field, Rank)
```

---

# Field $\times$ Rank: proportional
```{r}
d50[[1]] %$% table(Field, Rank) %>% prop.table(margin = 1)
```


---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT