---
title: "Table 2"
author: "Gerko Vink"
date: Mean score and prevalence^^ of Responsible Research Practices (RRP) stratified by Disciplinary Gender, Research and Research
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptive tables
library(tibble)   # Tibbles
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
options(DT.options = list(pageLength = 50)) # table options
```

---

# Means
```{r echo = FALSE}
Support <- d50[[1]] %>% #RRP has no missings -so use 1st imputed set
  select(starts_with("R"), Support) %>% 
  select(-Rank, -Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_")) %>% # exclude raw
  melt(id.vars = "Support", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Support, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, mean, ci, m.ci) 

mci.Support <- Support %>% dcast(Practices ~ Support, value.var = "m.ci") %>% 
  rename(`Support (Yes)` = Yes, `Support (No)` = No)
```
```{r echo = FALSE}
Gender <- d50[[1]] %>% #RRP has no missings -so use 1st imputed set
  select(starts_with("R"), Gender) %>% 
  select(-Rank, -Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_"))%>% # exclude raw
  melt(id.vars = "Gender", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Gender, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, Gender, mean, ci, m.ci) 

mci.Gender <- Gender %>% dcast(Practices ~ Gender, value.var = "m.ci") %>% .[, c(1, 4, 3, 2)]
```

```{r echo = FALSE}
Research <- d50[[1]] %>% #RRP has no missings -so use 1st imputed set
  select(starts_with("R"), Research) %>% 
  select(-Rank) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_")) %>% # exclude raw
  melt(id.vars = "Research", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Research, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1)) %>% 
  select(Practices, Research, mean, ci) 

mci.Research <- Research %>% mutate(m.ci = paste(mean, ci, sep = " ")) %>% dcast(Practices ~ Research, value.var = "m.ci") %>% 
  rename(`Research (Yes)` = Yes, `Research (No)` = No)
```

```{r echo = FALSE}
Means <- merge(mci.Gender, mci.Research, by.x = "Practices")
Means <- merge(Means, mci.Support, by.x = "Practices")

datatable(Means)
Means
```

---

# Prevalence of RRP items
```{r echo = FALSE}
p.test <- function(x){
  t <- suppressWarnings(prop.test(x))
  paste(round(t$estimate*100, 1),
        paste("(", round(t$conf.int[1]*100, 1), ",", round(t$conf.int[2]*100, 1), ")", sep = ""))
}
p.fun <- function(x){
  if(sum(x > 4) == 0) {
    return("none")
    } else {
  table(x > 4) %>% .[c(2, 1)] %>% t() %>% p.test
  }
}

Prevalence_RRP_Support <- d50[[1]] %>% #RRP has no missings -so use 1st imputed set
  select(starts_with("R"), Support) %>% 
  select(-Rank, -Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_")) %>%
  group_by(Support) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[-1, ] %>% 
  as.data.frame() %>% 
  `colnames<-`(names(Means)[7:8])
  
Prevalence_RRP_Gender <- d50[[1]] %>% #RRP has no missings -so use 1st imputed set
  select(starts_with("R"), Gender) %>% 
  select(-Rank, -Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_")) %>%
  group_by(Gender) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t()  %>% 
  .[-1, 3:1] %>% as.data.frame() %>% 
  `colnames<-`(names(Means)[2:4])

Prevalence_RRP_Research <- d50[[1]] %>% #RRP has no missings -so use 1st imputed set
  select(starts_with("R"), Research) %>% 
  select(-Rank) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_")) %>%
  group_by(Research) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[-1, ] %>% 
  as.data.frame() %>% 
  `colnames<-`(names(Means)[5:6])

prevalence <- cbind(Prevalence_RRP_Gender, 
                    Prevalence_RRP_Research, 
                    Prevalence_RRP_Support) %>% 
  .[c(1, 6, 8, 10, 9, 3, 7, 11, 2, 4, 5), ] #correct row order
prevalence %>% datatable()
prevalence
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT