---
title: "Table 2"
author: "Gerko Vink"
date: "Correlations between the explanatory variable scales"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptive tables
library(tibble)   # Tibbles
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
options(DT.options = list(pageLength = 50)) # table options
```

```{r echo = FALSE}
fisher.trans <- function(x) 1/2 * log((1 + x) / (1 - x))
fisher.backtrans <- function(x) (exp(2 * x) - 1) / (exp(2 * x) + 1)

cor <- d50 %>%
  map(~.x %>% 
        select(SciNorms, PeerNorms, WorkPress, PubPress, FundPress, Competitive, DetectCol, DetectRev, MentSurv, MentResp, OrgJust) %>% 
        stats::cor(use = "pairwise.complete.obs") %>%
        fisher.trans)
cor.rect <- Reduce("+", cor) / length(cor) # m is equal to the length of the list
cor <- fisher.backtrans(cor.rect)
diag(cor) <- 1
cor %>% round(2)
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT