---
title: "Table 2"
author: "Gerko Vink"
date: Mean score and prevalence^^  of Responsible Research Practices (RRP), Falsification, and Fabrication stratified by Disciplinary Field and Academic Rank
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptive tables
library(tibble)   # Tibbles
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
options(DT.options = list(pageLength = 50)) # table options
```

```{r echo = FALSE}
## RR functions
RR2 <- function(df){
  df <- na.omit(df)
  y  <- df$Freq
  n  <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  Q <- P %x% P
  phat <- solve(Q) %*% pobs
  varp <- (n - 1)^-1 * solve(Q) %*% (diag(pobs) -  pobs %*% t(pobs)) %*% t(solve(Q))
  min95 <- phat - 1.96*sqrt(diag(varp))
  max95 <- phat + 1.96*sqrt(diag(varp))
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat, 3), paste("(", round(min95, 3), ",", round(max95, 3), ")", sep = "")))
}

RR1 <- function(df){
  y <- df$Freq
  n <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  phat <- solve(P) %*% pobs
  varp <- prod(pobs)/(n*(P[2,2]-P[2,1])^2)
  min95 <- phat - 1.96*sqrt(varp)
  max95 <- phat + 1.96*sqrt(varp)
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat, 3), paste("(", round(min95, 3), ",", round(max95, 3), ")", sep = "")))
}
```

---

# Means
```{r echo = FALSE}
Overall <- d50[[1]] %>% #RRP has no missings -so use 1st imputed set
  select(starts_with("R")) %>% 
  select(-Rank, -Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_"), RRP_ave) %>% 
  melt(variable.name = "Practices") %>% 
  group_by(Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, mean, ci, m.ci) 
mci.overall <- Overall %>% select(Practices, m.ci) %>% rename(Overall = m.ci)
```
```{r echo = FALSE}
Field <- d50[[1]] %>% 
  select(Field, starts_with("R")) %>% 
  select(-Rank, -Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_"), RRP_ave) %>%  # exclude raw
  melt(id.vars = "Field", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Field, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, Field, mean, ci, m.ci) 

mci.Field <- Field %>% dcast(Practices ~ Field, value.var = "m.ci") %>% .[, c(1, 5, 2, 4, 3)]
```

```{r echo = FALSE}
Rank <- d50[[1]] %>% 
  select(Rank, starts_with("R")) %>% 
  select(-Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_"), RRP_ave) %>%  # exclude raw
  melt(id.vars = "Rank", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Rank, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1)) %>% 
  select(Practices, Rank, mean, ci) 

mci.Rank <- Rank %>% mutate(m.ci = paste(mean, ci, sep = " ")) %>% dcast(Practices ~ Rank, value.var = "m.ci")
```

```{r echo = FALSE}
Means <- merge(mci.Field, mci.Rank, by.x = "Practices")
Means <- merge(Means, mci.overall, by.x = "Practices")
Means <- Means[c(5, 3, 1, 10, 7, 11, 4, 8, 2, 9, 6, 12), ]
datatable(Means)
Means
```

---

# Prevalence of RRP items
```{r echo = FALSE}
p.test <- function(x){
  t <- suppressWarnings(prop.test(x))
  paste(round(t$estimate * 100, 1),
        paste("(", round(t$conf.int[1]*100, 1), ",", round(t$conf.int[2]*100, 1), ")", sep = ""))
}
p.fun <- function(x){
  table(x > 4) %>% .[c(2, 1)] %>% t() %>% p.test
}

Prevalence_RRP_Overall <- d50[[1]] %>% 
  select(starts_with("R")) %>% 
  select(-Rank, -Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_"))  %>%
  summarise_all(list(prevalence = p.fun)) %>% t() %>% 
  data.frame(Overall = .)

Prevalence_RRP_Field <- d50[[1]] %>% 
  select(Field, starts_with("R")) %>% 
  select(-Rank, -Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_"))  %>%
  group_by(Field) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[, c(4, 1, 3, 2)] %>% 
  .[-1, ] %>% as.data.frame() %>% 
  `colnames<-`(names(Means)[2:5])

Prevalence_RRP_Rank <- d50[[1]] %>% 
  select(Rank, starts_with("R")) %>% 
  select(-Research) %>% 
  select(-RRfabr, -RRfals) %>% 
  select(!contains("_")) %>%
  group_by(Rank) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[-1, ] %>% 
  as.data.frame() %>% 
  `colnames<-`(names(Means)[6:8])

prevalence <- cbind(Prevalence_RRP_Field, 
                    Prevalence_RRP_Rank, 
                    Prevalence_RRP_Overall)
prevalence %>% datatable()
prevalence
```

---

<!-- # Prevalence of any RRP and Randomized Response -->
<!-- ```{r echo = FALSE} -->
<!-- RRP1_overall <- d50[[1]] %$% #RRP has no missings -so use 1st imputed set -->
<!--   table(1 - RRP_1)  %>% p.test -->
<!-- Fals_overall <- d50[[1]] %$%  -->
<!--   table(RRfals) %>%  -->
<!--   melt(value.name = "Freq") %>%  -->
<!--   RR1() %>%  .$p.ci %>% .[2] -->
<!-- Fabr_overall <- d50[[1]] %$%  -->
<!--   table(RRfabr) %>%  -->
<!--   melt(value.name = "Freq") %>%  -->
<!--   RR1() %>%  .$p.ci %>% .[2] -->
<!-- FF_overall <- d50[[1]] %$%  -->
<!--   table(RRfals, RRfabr) %>%  -->
<!--   melt(value.name = "Freq") %>%  -->
<!--   RR2() %>% .$phat %>% .[2:4] %>% sum  -->

<!-- prev.overall <- data.frame(Overall = c(RRP1_overall, Fals_overall, Fabr_overall, round(FF_overall, 3))) -->
<!-- ``` -->
<!-- ```{r echo=FALSE} -->
<!-- RRP1_Field <- d50[[1]] %>%  -->
<!--   select(Field, RRP_1) %>%  -->
<!--   group_by(Field) %>%  -->
<!--   group_map(~ sapply(., table, simplify = TRUE)) %>%  -->
<!--   map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>%  -->
<!--   do.call(rbind, .) %>% t() %>% as.data.frame() %>%  -->
<!--   mutate(Indicator = "ANY_RRP") %>%  -->
<!--   .[, c(5, 4, 1, 3, 2)] #reorder, cf. table -->
<!-- Fals_Field <- d50[[1]] %>%  -->
<!--   group_by(Field) %>%  -->
<!--   group_map(~.x %$%  -->
<!--               table(RRfals) %>%  -->
<!--               melt(value.name = "Freq")) %>%  -->
<!--               map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>%  -->
<!--    do.call(rbind, .) %>% t() %>% as.data.frame() %>%  -->
<!--   mutate(Indicator = "Falsification") %>%  -->
<!--   .[, c(5, 4, 1, 3, 2)] #reorder, cf. table -->
<!-- Fabr_Field <- d50[[1]] %>%  -->
<!--   group_by(Field) %>%  -->
<!--   group_map(~.x %$%  -->
<!--               table(RRfabr) %>%  -->
<!--               melt(value.name = "Freq")) %>%  -->
<!--               map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>%  -->
<!--    do.call(rbind, .) %>% t() %>% as.data.frame() %>%  -->
<!--   mutate(Indicator = "Fabrication") %>%  -->
<!--   .[, c(5, 4, 1, 3, 2)] #reorder, cf. table -->
<!-- FF_Field <- d50[[1]] %>%  -->
<!--   group_by(Field) %>%  -->
<!--   group_map(~.x %$%  -->
<!--               table(RRfals, RRfabr) %>%  -->
<!--               melt(value.name = "Freq")) %>%  -->
<!--               map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>%  -->
<!--    do.call(rbind, .) %>% t() %>% as.data.frame() %>%  -->
<!--   mutate(Indicator = "FF") %>%  -->
<!--   .[, c(5, 4, 1, 3, 2)] #reorder, cf. table -->

<!-- prev.Field <- rbind(RRP1_Field, Fals_Field, Fabr_Field, FF_Field) -->
<!-- colnames(prev.Field)[2:5] <- names(Means)[2:5] -->
<!-- ``` -->
<!-- ```{r echo=FALSE} -->
<!-- RRP1_Rank <- d50[[1]] %>%  -->
<!--   select(Rank, RRP_1) %>%  -->
<!--   group_by(Rank) %>%  -->
<!--   group_map(~ sapply(., table, simplify = TRUE)) %>%  -->
<!--   map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>%  -->
<!--   do.call(rbind, .) %>% t() %>% as.data.frame() %>%  -->
<!--   mutate(Indicator = "ANY_RRP")  -->
<!-- Fals_Rank <- d50[[1]] %>%  -->
<!--   group_by(Rank) %>%  -->
<!--   group_map(~.x %$%  -->
<!--               table(RRfals) %>%  -->
<!--               melt(value.name = "Freq")) %>%  -->
<!--               map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>%  -->
<!--    do.call(rbind, .) %>% t() %>% as.data.frame() %>%  -->
<!--   mutate(Indicator = "Falsification")  -->
<!-- Fabr_Rank <- d50[[1]] %>%  -->
<!--   group_by(Rank) %>%  -->
<!--   group_map(~.x %$%  -->
<!--               table(RRfabr) %>%  -->
<!--               melt(value.name = "Freq")) %>%  -->
<!--               map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>%  -->
<!--    do.call(rbind, .) %>% t() %>% as.data.frame() %>%  -->
<!--   mutate(Indicator = "Fabrication")  -->
<!-- FF_Rank <- d50[[1]] %>%  -->
<!--   group_by(Rank) %>%  -->
<!--   group_map(~.x %$%  -->
<!--               table(RRfals, RRfabr) %>%  -->
<!--               melt(value.name = "Freq")) %>%  -->
<!--               map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>%  -->
<!--    do.call(rbind, .) %>% t() %>% as.data.frame() %>% round(3) %>%  -->
<!--   mutate(Indicator = "FF")  -->

<!-- prev.Rank <- rbind(RRP1_Rank, Fals_Rank, Fabr_Rank, FF_Rank)[, c(4, 1, 2, 3)] -->
<!-- colnames(prev.Rank)[2:4] <- names(Means)[6:8] -->
<!-- ``` -->

<!-- ```{r} -->
<!-- prevalence <- merge(prev.Field, prev.Rank, by.x = "Indicator") -->
<!-- cbind(prevalence, prev.overall) %>%  -->
<!--   datatable() -->
<!-- cbind(prevalence, prev.overall) -->
<!-- ``` -->

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT