---
title: "1. Data import and preperation"
author: "Gerko Vink"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---
  
<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>

---

This script reads in the data set `244406978_NSRI_dataset_27012021.sav` the data and stores the data frame as an `R`-workspace. We transfer the data to an `R`-friendly format to facilitate speedy data processing in `R` for all further data imputation and analyses steps. 

---


# Packages used
For this document we use the following packages
```{r}
library(haven) # Data import/export
library(dplyr) # Data manipulation
library(magrittr) # Pipes
```

---

# Importing the data
We use function `read_sav` from package `haven` to import the SPSS file produced by Kantar into `R`. 
```{r}
raw_data <- read_sav("244406978_NSRI_dataset_27012021.sav")
```
We name the resulting object `NSRI_data`

---

# Creating a data frame
We create an accessible data frame that will serve as the basis for imputation and analysis. 
```{r}

NSRI_df <- raw_data %>% as_factor %>% zap_labels() %>% zap_formats() %>% zap_label()
```

---

# Convert factors to numeric
We convert the questinable research practices items and the responsible research practices items to factors. 
```{r}
which <- names(raw_data)[11:107] # all questionaire items F and RP
NSRI_df[, which] %<>% mutate_if(., is.factor, as.numeric)
```

---

# Make `ID` a character vector
```{r}
NSRI_df %<>% mutate(ID = as.character(ID)) 
```

---

# Exporting the workspace
We export the objects `NSRI_df` and `raw_data` in an `R` workspace to the `\Workspaces\` directory in the project root. The resulting workspace name mirrors the name of this document. 
```{r}
save(NSRI_df, raw_data, file = "Workspaces/1. Data import and preparation.Rdata")
```


---

End of document. 

---

```{r}
sessionInfo()
```

