---
title: "5. Preparation Imputed Datasets"
author: "Maarten Cruyff"
output: 
  html_document:
   toc: true
   toc_float: true
   toc_depth: 5
   theme: paper
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 8px;
}

</style>



---

This documents prepares the 50 imputed data sets for statistical analysis.

---

# Packages used

```{r message=F}
library(dplyr)
library(purrr)
library(magrittr)
library(mice)
library(psych)
```

# Importing data

Loading the workspace with the `3. Data imputation.Rdata` with the 50 imputed data sets.

```{r}
load("Workspaces/3. Data imputation.Rdata")
```

---

# Make data object

Storing the 50 imputed data sets in the list `d50`.

```{r}
d50 <- imp %>% 
  complete("all") 
```

---


# Deleting unused variables

```{r}
d50 <- d50 %>% 
  map(select, -ID, -FinishDate, -IC1, -IC2, -D1, -V, -RRtest1, -RRtest2)
```


---

# Names RRP's and QRP's

Vectors that will be used to rename RP1 to RP22 in intelligible names for the RPPs (starting with the letter R) and QRPs (starting with the letter Q)

```{r}
rrp <- c("RDisclFunds", "RCorrectPub", "RAuthorship", "ROpenData", "RKeepRecord", 
         "RPreReg", "RDataManage", "ROpenAccess", "RCiteSource", "ROpenCode", "RErrorCheck")
qrp <- c("QAttention", "QSupervision", "QResDesign", "QUnfairRev", "QUnsubstClaims", 
         "QCiteSource", "QResNotes", "QConcealDetails", "QNoReSubmit", "QConcealFlaws", "QSelectCites")
```


# Relocating and renaming variables

Order data sets on (old names in parenthesis):

1. Background variables (5): "Field", "Rank", "Gender", "Research", "Support" (Group)

2. Explanatory variables (75): ordered from 1 to 75

3. RRP variables (11): names in `rrp` with suffix `_raw` to indicate that Not Applicable are coded 0.

4. QRP variables (11): names in `rrp` with suffix `_raw` to indicate that Not Applicable are coded 0.

5. RR variables (2): "RRfabr" (RR1) and "RRfals" (RR2)

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        relocate(F1:F18, .before = F19)%>% 
        relocate(Group,  .before = F1) %>% 
        relocate(RP1, RP2, RP4, RP6, RP9, RP12, RP15, RP16, RP17, RP19, RP21, .before = RP3) %>%  
        rename_at(vars(D2:Group), ~ c("Field", "Rank", "Gender", "Research", "Support")) %>%  
        rename_at(vars(RP1:RP21), ~ paste0(rrp, "_raw")) %>% 
        rename_at(vars(RP3:RP22), ~ paste0(qrp, "_raw")) %>%
        rename_at(vars(RR1, RR2), ~ c("RRfabr", "RRfals")))
names(d50[[1]])
```

---


# Recoding variables


## Background variables

Shortening labels of background variables for use in tables and graphs.

```{r}
d50 <- d50 %>%  
  map(~ .x %>% 
        mutate_at(vars(Field), recode_factor, 
                  `Social and Behavioral Sciences` = "Soc & Beh",
                  `Arts and Humanities` = "Arts & Hum",
                  `Engineering and Natural Sciences` = "Eng & Nat",
                  `Biomedical and Life Sciences` = "Bio & Life") %>% 
        mutate_at(vars(Rank), recode_factor, 
                  `PhD student or junior researcher` = "PhD",
                  `Postdoctoral researcher, Assistant Professor, Physician Researcher or Lecturer Researcher` = "Postdoc",
                  `Associate Professor or Full Professor` = "Prof") %>% 
        mutate_at(vars(Gender), recode_factor, 
                  `Other / Do not wish to disclose` = "Undisclosed")%>%  
        mutate_at(vars(Support), recode_factor, 
                  `Joining group` = "Yes",
                  `Non-joining group` = "No"))
```



---


## Explanatory variables 

Set Not Applicable (score = 0) to `NA`, and reverse scores of contra-indicative items.

```{r}
d50 <- d50 %>%  
  map(~ .x %>% 
        mutate_at(vars(F1:F75), na_if, 0) %>% 
        mutate_at(vars(F19, F28, F32, F40, F44, F45, F53, F54, F58, F61), ~{8 - .}))
```

---


## RR variables


Recoding the answers "triangle"  and "circle" of the randomized response items into 0 (no) and 1 (yes).

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate_at(vars(RRfabr), recode, `circle` = 0, `triangle` = 1) %>% 
        mutate_at(vars(RRfals), recode, `circle` = 1, `triangle` = 0))
```

---



# Adding new variables

Recoding the 0 scores (Not Applicable) in the raw RRP/QRP variables into 1 ("Never")

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate_at(vars(!!!syms(paste0(rrp, "_raw"))), list(r = ~ recode(., `0` = 1))) %>% 
        rename_at(vars(ends_with(("_raw_r"))), ~ gsub("_raw_r", "", .x)) %>% 
        mutate_at(vars(!!!syms(paste0(qrp, "_raw"))), list(q = ~ recode(., `0` = 1))) %>% 
        rename_at(vars(ends_with(("_raw_q"))), ~ gsub("_raw_q", "", .x))) 
```

---



## Mean scores RRP/QRP's

Computation of the mean score scores on the RRPs and the QRPs:

- "RRP": average score on RRP's, with `NA` with one or more score missing (Not Available) 

- "QRP": average score on QRP's, with `NA` with one or more score missing (Not Available) 


```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate(RRP_ave = rowMeans(cbind(!!!syms(rrp)), na.rm = T)) %>% 
        mutate(QRP_ave = rowMeans(cbind(!!!syms(qrp)), na.rm = T))) 
```

---


## At least one QRP

- "QRP_1": takes value 1 if at any of the QRPs has a score > 4, and 0 otherwise 

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate(QRP_1 = rowSums(cbind(!!!syms(qrp)) > 4)) %>% 
        mutate(QRP_1 = if_else(QRP_1 == 0, 0, 1)))
```


---


## Explanatory variable scales

Explanatory variables scales are computed as the 1st component of the PCA of the corresponding items, where: 

- the component score are based on the pairwise correlations between the items

- the component scores are a weighed average of the item scores

- with the weights determined such that the scale optimally discriminates between subjects

- cases with an Not Applicable on any of the scale items will get an `NA` (missing value) score on the corresponding scale





```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate(principal(cbind( F1,  F2,  F3,  F4,  F5, F6, F7,  F8, F9)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(SciNorms = "PC1"),
               principal(cbind(F10, F11, F12, F13, F14, F15, F16, F17, F18)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(PeerNorms = "PC1"), 
               principal(cbind(F19, F20, F21)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(WorkPress = "PC1"), 
               principal(cbind(F22, F23, F24, F25, F26, F27)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(PubPress = "PC1"), 
               principal(cbind(F28, F29, F30, F31, F32, F33)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(FundPress = "PC1"), 
               principal(cbind(F40, F41, F42, F43, F44, F45)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(Competitive = "PC1"), 
               principal(cbind(F64, F65, F66, F67, F68, F69)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(DetectCol = "PC1"), 
               principal(cbind(F70, F71, F72, F73, F74, F75)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(DetectRev = "PC1"),
               principal(cbind(F34, F35, F36, F37, F38, F39, 
                               F46, F47, F48, F49, F50, F51)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(Mentoring = "PC1"), 
               principal(cbind(F52, F53, F54, F55, F56, F57, F58, F59, 
                               F60, F61, F62, F63)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(OrgJust = "PC1"),
               principal(cbind(F34, F35, F36, F37, F38, F39)) %>%
                 pluck("scores") %>% as.data.frame %>% 
                 rename(MentSurv = "PC1"),
               principal(cbind(F46, F47, F48, F49, F50, F51)) %>%
                 pluck("scores") %>% as.data.frame %>% 
                 rename(MentResp = "PC1"),
               principal(cbind(F52, F53, F54, F55, F56, F57)) %>%
                 pluck("scores") %>% as.data.frame %>% 
                 rename(DistJust = "PC1"),
               principal(cbind(F58, F59, F60, F61, F62, F63)) %>%
                 pluck("scores") %>% as.data.frame %>% 
                 rename(ProcJust = "PC1")
               ))

```


In contrast to the original data analysis plan 10 instead 12 scales are computed

- `Mentoring`  is composed of the 12 items of the original scales `RespMent` + `SurvMent`

- `OrgJust` is composed of the 12 items of the original scales `DistJust` + `ProcJust`

The reason for this is that the original scales are highly correlated (see below), which 

- means that they measure similar constructs and

- that including these scales separately in regression analyses may result in multicollinearity problems

```{r}
d50[[1]] %$% cor(cbind(OrgJust, DistJust, ProcJust)) %>% round(., 2)
```

```{r}
d50[[1]] %$% cor(cbind(Mentoring, MentSurv, MentResp)) %>% round(., 2)
```

Deleting the 4 superfluous scale **NOT EXECUTED**

```{r}
#d50 <- d50 %>% 
#  map(select, - MentSurv, -MentResp, -DistJust, - ProcJust) #Dec 15, 2022 GV checked JW
```


---


## Replacement scale missings 

Missing values on the scales due to Not Applicables are replaced by the means of the corresponding scaled items, ignoring the Not Applicables.  

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate_at(vars(F28:F75), list(s = ~ scale(.))) %>% 
        mutate(m         = rowMeans(cbind(F28_s, F29_s, F30_s, F31_s, F32_s, F33_s), 
                                    na.rm = T),
               FundPress = if_else(is.na(FundPress), m, FundPress),
               m         = rowMeans(cbind(F64_s, F65_s, F66_s, F67_s, F68_s, F69_s), 
                                    na.rm = T),
               DetectCol = if_else(is.na(DetectCol), m, DetectCol),
               m         = rowMeans(cbind(F70_s, F71_s, F72_s, F73_s, F74_s, F75_s), 
                                    na.rm = T),
               DetectRev = if_else(is.na(DetectRev), m, DetectRev),
               m         = rowMeans(cbind(F34_s, F35_s, F36_s, F37_s, F38_s, F39_s, 
                                          F46_s, F47_s, F48_s, F49_s, F50_s, F51_s), 
                                    na.rm = T),
               Mentoring = if_else(is.na(Mentoring), m, Mentoring),
               m         = rowMeans(cbind(F34_s, F35_s, F36_s, F37_s, F38_s, F39_s), 
                                    na.rm = T),
               MentSurv = if_else(is.na(MentSurv), m, MentSurv),
               m         = rowMeans(cbind(F46_s, F47_s, F48_s, F49_s, F50_s, F51_s), 
                                    na.rm = T),
               MentResp = if_else(is.na(MentResp), m, MentResp),
               m         = rowMeans(cbind(F52_s, F53_s, F54_s, F55_s, F56_s, F57_s, 
                                          F58_s, F59_s, F60_s, F61_s, F62_s, F63_s),  
                                    na.rm = T),
               OrgJust   = if_else(is.na(OrgJust), m, OrgJust)) %>% 
        select(-(F28_s:F75_s), -m))
```


# Variables in data sets

```{r}
names(d50[[1]])
```

# Data summary 

Summary of the 1st of the 50 data sets.

```{r}
summary(d50[[1]])
```


# Exporting workspace

```{r}
save(d50, file = "Workspaces/5. Preparation Imputed Datasets.Rdata")
```

```{r}
sessionInfo()
```

