---
title: "5. Preparation Imputed Datasets"
author: "Maarten Cruyff"
output: 
  html_document:
   toc: true
   toc_float: true
   toc_depth: 5
   theme: paper
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>



---

This documents prepares the 50 imputed data sets for statistical analysis.

---

# Packages used

```{r message=F}
library(dplyr)
library(purrr)
library(magrittr)
library(mice)
library(psych)
```

# Importing data

Loading the workspace with the `3. Data imputation.Rdata` with the 50 imputed data sets.

```{r}
load("Workspaces/3. Data imputation.Rdata")
```

---

# Make data object

The 50 imputed data sets are stored in the list `d50`.

```{r}
d50 <- imp %>% 
  complete("all") 
```

---


# Deleting unused variables

```{r}
d50 <- d50 %>% 
  map(select, -ID, -FinishDate, -IC1, -IC2, -D1, -V, -RRtest1, -RRtest2)
```


---

# Names RRP's and QRP's

```{r}
rrp <- c("RDisclFunds", "RCorrectPub", "RAuthorship", "ROpenData", "RKeepRecord", 
         "RPreReg", "RDataManage", "ROpenAccess", "RCiteSource", "ROpenCode", "RErrorCheck")
qrp <- c("QAttention", "QSupervision", "QResDesign", "QUnfairRev", "QUnsubstClaims", 
         "QCiteSource", "QResNotes", "QConcealDetails", "QNoReSubmit", "QConcealFlaws", "QSelectCites")
```


# Relocating and renaming variables

Order data sets on (old names in parenthesis):

1. Background variables (5): "Field", "Rank", "Gender", "Research", "Support" (Group)

2. Explanatory variables (75): ordered from 1 to 75

3. RRP variables (11): names in `rrp` (RP1, RP2, RP4, RP6, RP9, RP12, RP15, RP16, RP17, RP19, RP21)

4. QRP variables (11): names in `rrp`  (RP3, RP5, RP7, RP8, RP10, RP11, RP13, RP14, RP18, RP20, RP22)

5. RR variables (2): "RRfabr" (RR1) and "RRfals" (RR2)

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        relocate(F1:F18, .before = F19)%>% 
        relocate(Group,  .before = F1) %>% 
        relocate(RP1, RP2, RP4, RP6, RP9, RP12, RP15, RP16, RP17, RP19, RP21, .before = RP3) %>%  
        rename_at(vars(D2:Group), ~ c("Field", "Rank", "Gender", "Research", "Support")) %>%  
        rename_at(vars(RP1:RP21), ~ paste0(rrp, "_raw")) %>% 
        rename_at(vars(RP3:RP22), ~ paste0(qrp, "_raw")) %>%
        rename_at(vars(RR1, RR2), ~ c("RRfabr", "RRfals")))
names(d50[[1]])
```

---


# Recoding variables


## Background variables

Shorten labels of background variables for use in tables and graphs.

```{r}
d50 <- d50 %>%  
  map(~ .x %>% 
        mutate_at(vars(Field), recode_factor, 
                  `Social and Behavioral Sciences` = "Soc & Beh",
                  `Arts and Humanities` = "Arts & Hum",
                  `Engineering and Natural Sciences` = "Eng & Nat",
                  `Biomedical and Life Sciences` = "Bio & Life") %>% 
        mutate_at(vars(Rank), recode_factor, 
                  `PhD student or junior researcher` = "PhD",
                  `Postdoctoral researcher, Assistant Professor, Physician Researcher or Lecturer Researcher` = "Postdoc",
                  `Associate Professor or Full Professor` = "Prof") %>% 
        mutate_at(vars(Gender), recode_factor, 
                  `Other / Do not wish to disclose` = "Undisclosed")%>%  
        mutate_at(vars(Support), recode_factor, 
                  `Joining group` = "Yes",
                  `Non-joining group` = "No"))
```



---


## Explanatory variables 

Set Not Applicable (score = 0) to `NA`, and reverse scores of contra-indicative items.

```{r}
d50 <- d50 %>%  
  map(~ .x %>% 
        mutate_at(vars(F1:F75), na_if, 0) %>% 
        mutate_at(vars(F19, F28, F32, F40, F44, F45, F53, F54, F58, F61), ~{8 - .}))
```

---


## RR variables


Recoding the answers  "triangle"  and "circle" into 0 (no) and 1 (yes)

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate_at(vars(RRfabr), recode, `circle` = 0, `triangle` = 1) %>% 
        mutate_at(vars(RRfals), recode, `circle` = 1, `triangle` = 0))
```

---



# Adding new variables

 Recoding NA's in RRP/QRP's

- For RRP's: 0 (Not Applicable) changed into 7 (Always)

- For QRP's: 0 (Not Applicable) changed into 1 (Never)

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate_at(vars(!!!syms(paste0(rrp, "_raw"))), list(r = ~ recode(., `0` = 7))) %>% 
        rename_at(vars(ends_with(("_raw_r"))), ~ gsub("_raw_r", "", .x)) %>% 
        mutate_at(vars(!!!syms(paste0(qrp, "_raw"))), list(q = ~ recode(., `0` = 1))) %>% 
        rename_at(vars(ends_with(("_raw_q"))), ~ gsub("_raw_q", "", .x))) 
```

---

```{r}
names(d50[[1]])
```


## Total scores RRP/QRP's

Computation of the total scores on RRP's and QRP's:

- "RRP": average score on RRP's, with `NA` with one or more score missing (Not Available) 

- "QRP": average score on QRP's, with `NA` with one or more score missing (Not Available) 


```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate(RRP_ave = rowMeans(cbind(!!!syms(rrp)), na.rm = T)) %>% 
        mutate(QRP_ave = rowMeans(cbind(!!!syms(qrp)), na.rm = T))) 
```

---


## At least one QRP

- "QRP1": 1 if score 7 on at least one QRP, and 0 otherwise 

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate(QRP_1 = rowSums(cbind(!!!syms(qrp)) == 7)) %>% 
        mutate(QRP_1 = if_else(QRP_1 == 0, 0, 1)))
```


---


## Explanatory variable scales

Explanatory variables scales are computed as the 1st component of the PCA of the corresponding items. 

Instead of two, single scales are composed for: 

- Mentoring  (Responsible + Survival)

- Organizational Justice (Distributional + Procedural)



```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate(principal(cbind( F1,  F2,  F3,  F4,  F5, F6, F7,  F8, F9)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(SciNorms = "PC1"),
               principal(cbind(F10, F11, F12, F13, F14, F15, F16, F17, F18)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(PeerNorms = "PC1"), 
               principal(cbind(F19, F20, F21)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(WorkPress = "PC1"), 
               principal(cbind(F22, F23, F24, F25, F26, F27)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(PubPress = "PC1"), 
               principal(cbind(F28, F29, F30, F31, F32, F33)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(FundPress = "PC1"), 
               principal(cbind(F40, F41, F42, F43, F44, F45)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(Competitive = "PC1"), 
               principal(cbind(F64, F65, F66, F67, F68, F69)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(DetectCol = "PC1"), 
               principal(cbind(F70, F71, F72, F73, F74, F75)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(DetectRev = "PC1"),
               principal(cbind(F34, F35, F36, F37, F38, F39, F46, F47, F48, F49, F50, F51)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(Mentoring = "PC1"), 
               principal(cbind(F52, F53, F54, F55, F56, F57, F58, F59, F60, F61, F62, F63)) %>% 
                 pluck("scores") %>% as.data.frame %>% 
                 rename(OrgJust = "PC1")))

```

---


## Replacement scale missings 

Missing values on the scales due to Not Applicables are replaced by the means of the corresponding scaled items, ignoring the Not Applicables.  

```{r}
d50 <- d50 %>% 
  map(~ .x %>% 
        mutate_at(vars(F28:F75), list(s = ~ scale(.))) %>% 
        mutate(m         = rowMeans(cbind(F28_s, F29_s, F30_s, F31_s, F32_s, F33_s), na.rm = T),
               FundPress = if_else(is.na(FundPress), m, FundPress),
               m         = rowMeans(cbind(F64_s, F65_s, F66_s, F67_s, F68_s, F69_s), na.rm = T),
               DetectCol = if_else(is.na(DetectCol), m, DetectCol),
               m         = rowMeans(cbind(F70_s, F71_s, F72_s, F73_s, F74_s, F75_s), na.rm = T),
               DetectRev = if_else(is.na(DetectRev), m, DetectRev),
               m         = rowMeans(cbind(F34_s, F35_s, F36_s, F37_s, F38_s, F39_s, F46_s, F47_s, F48_s, F49_s, F50_s, F51_s), na.rm = T),
               Mentoring = if_else(is.na(Mentoring), m, Mentoring),
               m         = rowMeans(cbind(F52_s, F53_s, F54_s, F55_s, F56_s, F57_s, F58_s, F59_s, F60_s, F61_s, F62_s, F63_s),  na.rm = T),
               OrgJust   = if_else(is.na(OrgJust), m, OrgJust)) %>% 
        select(-(F28_s:F75_s), -m))
```


# Variables in data sets

```{r}
names(d50[[1]])
```

# Summary data set 

```{r}
summary(d50[[1]])
```


# Exporting workspace

```{r}
save(d50, file = "Workspaces/5. Preparation Imputed Datasets.Rdata")
```

```{r}
sessionInfo()
```

