---
title: "A10 Prevalence of F2 Falsification"
author: "Gerko Vink"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>

---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptives
library(tibble)   # Dataframes on steroids
library(gtools)   # Useful tools
library(DT)       # HTML tables
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../Workspaces/3. Data imputation.Rdata")
load(file = "../Workspaces/2. Data inspection.Rdata")
```

---
## Prevalence

---

### Overall
We calculate the prevalence of any Falsification as
```{r}
# Use RRreg::RRuni
raw_data %$% #F1 has no missings - so use first imputed set
  RRuni(RR2 - 1, model = "Warner", p = 1/6) #-1 because RRuni needs vector of 0 and 1 - not 1 and 2

# Custom function
RResp <- function(input, prob){
  yes <- input %>% table %>% prop.table %>% .[1]
  true <- (yes + prob - 1) / (2 * prob - 1)
  return(true)
}

RResp(raw_data$RR2, prob = 5/6)

table(raw_data$RR2)
```

---

### By disciplinary field
We calculate the prevalence of any Falsification as
```{r}
mice::complete(imp, 1) %>% #F1 has no missings - so use first imputed set
  group_by(D2) %>% 
  summarise(true_proportion = RResp(RR2, prob = 5/6)) 
```

---

### By rank
We calculate the prevalence of any Falsification as
```{r}
mice::complete(imp, 1) %>% #F1 has no missings - so use first imputed set
  group_by(D3) %>% 
  summarise(true_proportion = RResp(RR2, prob = 5/6)) 
```

---

### By gender identification
We calculate the prevalence of any Falsification as
```{r}
mice::complete(imp, 1) %>% #F1 has no missings - so use first imputed set
  group_by(D4) %>% 
  summarise(true_proportion = RResp(RR2, prob = 5/6)) 
```
---

### By  empirical research engagement
We calculate the prevalence of any Falsification as
```{r}
mice::complete(imp, 1) %>% #F1 has no missings - so use first imputed set
  group_by(D5) %>% 
  summarise(true_proportion = RResp(RR2, prob = 5/6)) 
```

---

### By institutional support
We calculate the prevalence of any Falsification as
```{r}
mice::complete(imp, 1) %>% #F1 has no missings - so use first imputed set
  group_by(Group) %>% 
  summarise(true_proportion = RResp(RR2, prob = 5/6)) 
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT


