---
title: "A2 Relative Prevalence of QRP"
author: "Gerko Vink"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
```

---

# Load the data
```{r}
load(file = "../Workspaces/3. Data imputation.Rdata")
load(file = "../Workspaces/2. Data inspection.Rdata")
```

---

# QRP with `Not Applicable`'s
First, we create an indicator for all QRP
```{r}
QRP_set <- names(raw_data[86:107])[-c(1, 2, 4, 6, 9, 12, 15, 16, 17, 19, 21 )]
```

## Tables and plots

### Overall
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(all_of(QRP_set)) %>% 
  sapply(table)
```
Zero indicates not applicable

Then we calculate the proportional table
```{r}
p_tab <- function(x){prop.table(table(x)) %>% round(3)}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(all_of(QRP_set)) %>% 
  sapply(p_tab) %>%
  round(3)
```

Next, we create the stacked barplot. 
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(all_of(QRP_set)) %>% 
  sapply(table) %>% 
  melt(varnames = c("Response", "Practices")) %>% 
  mutate(Response = factor(Response),
         percentage = value / (sum(value)/11),
         Response = recode(Response, `0` = "Not Applicable", `1` = "1 Never", `7` = "7 Always")) %>% 
  ggplot(aes(x = Practices, y = percentage, fill = Response)) +
  geom_bar(stat = 'identity', position = "stack", colour="black") +
  geom_col(position = position_stack(reverse = FALSE)) + 
  scale_fill_brewer(palette = "Spectral", direction = -1) +
  theme_minimal()
```

---

### By Disciplinary Field
First, we grab the info from `D2`
```{r}
raw_data$D2 %>% var_label
raw_data$D2 %>% val_labels
```
Then we calculate a table for each of the labels in `D2`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(D2, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D2) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$D2 %>% val_labels %>% names
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(D2, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D2) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
barplotfun <- function(data){
  current <- sapply(out, function(x){identical(x, data)}) %>% which %>% names
  data %>% 
    melt(varnames = c("Response", "Practices")) %>% 
    mutate(Response = factor(Response),
           percentage = value / (sum(value)/11),
           Response = recode(Response, `0` = "Not Applicable", `1` = "1 Never", `7` = "7 Always")) %>% 
    ggplot(aes(x = Practices, y = percentage, fill = Response)) +
    geom_bar(stat = 'identity', position = "stack", colour="black") +
    geom_col(position = position_stack(reverse = FALSE)) + 
    scale_fill_brewer(palette = "Spectral", direction = -1) +
    theme_minimal() + 
    ggtitle(current)
}
lapply(out, barplotfun)
```

---

### By academic rank
First, we grab the info from `D3`
```{r}
raw_data$D3 %>% var_label
raw_data$D3 %>% val_labels
```
Then we calculate a table for each of the labels in `D3`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(D3, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D3) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$D3 %>% val_labels %>% names %>% .[1:3]
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(D3, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D3) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
lapply(out, barplotfun)
```


---

### By gender identification
First, we grab the info from `D4`
```{r}
raw_data$D4 %>% var_label
raw_data$D4 %>% val_labels
```
Then we calculate a table for each of the labels in `D4`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(D4, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D4) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$D4 %>% val_labels %>% names
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(D4, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D4) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
lapply(out, barplotfun)
```


---

### By empirical research engagement
First, we grab the info from `D5`
```{r}
raw_data$D5 %>% var_label
raw_data$D5 %>% val_labels
```
Then we calculate a table for each of the labels in `D5`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(D5, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D5) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$D5 %>% val_labels %>% names
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(D5, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D5) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
lapply(out, barplotfun)
```

---

### By institutional support
First, we grab the info from `Group`
```{r}
raw_data$Group %>% var_label
raw_data$Group %>% val_labels
```
Then we calculate a table for each of the labels in `Group`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(Group, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(Group) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$Group %>% val_labels %>% names
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(Group, all_of(QRP_set)) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(Group) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
lapply(out, barplotfun)
```

---

# QRP without `Not Applicable`'s

## Tables and plots

### Overall
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(all_of(QRP_set)) %>% 
  na_if(0) %>% 
  sapply(table)
```
Zero indicates not applicable

Then we calculate the proportional table
```{r}
p_tab <- function(x){prop.table(table(x)) %>% round(3)}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(all_of(QRP_set)) %>% 
  na_if(0) %>% 
  sapply(p_tab) %>%
  round(3)
```

Next, we create the stacked barplot. 
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(all_of(QRP_set)) %>% 
  na_if(0) %>% 
  sapply(p_tab) %>% 
  melt(varnames = c("Response", "Practices")) %>% 
  mutate(Response = factor(Response),
         percentage = value, 
         Response = recode(Response, `1` = "1 Never", `7` = "7 Always")) %>% 
  ggplot(aes(x = Practices, y = percentage, fill = Response)) +
  geom_bar(stat = 'identity', position = "stack", colour="black") +
  geom_col(position = position_stack(reverse = FALSE)) + 
  scale_fill_brewer(palette = "Spectral", direction = -1) +
  theme_minimal()
```

---

### By Disciplinary Field
First, we grab the info from `D2`
```{r}
raw_data$D2 %>% var_label
raw_data$D2 %>% val_labels
```
Then we calculate a table for each of the labels in `D2`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(D2, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D2) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$D2 %>% val_labels %>% names
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(D2, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D2) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
barplotfun <- function(data){
  current <- sapply(p.out, function(x){identical(x, data)}) %>% which %>% names
  data %>% 
    melt(varnames = c("Response", "Practices")) %>% 
    mutate(Response = factor(Response),
           percentage = value / (sum(value)/11),
           Response = recode(Response, `1` = "1 Never", `7` = "7 Always")) %>% 
    ggplot(aes(x = Practices, y = percentage, fill = Response)) +
    geom_bar(stat = 'identity', position = "stack", colour="black") +
    geom_col(position = position_stack(reverse = FALSE)) + 
    scale_fill_brewer(palette = "Spectral", direction = -1) + 
    theme_minimal() + 
    ggtitle(current)
}
lapply(p.out, barplotfun)
```

---

### By academic rank
First, we grab the info from `D3`
```{r}
raw_data$D3 %>% var_label
raw_data$D3 %>% val_labels
```
Then we calculate a table for each of the labels in `D3`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(D3, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D3) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$D3 %>% val_labels %>% names %>% .[1:3]
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(D3, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D3) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
lapply(p.out, barplotfun)
```


---

### By gender identification
First, we grab the info from `D4`
```{r}
raw_data$D4 %>% var_label
raw_data$D4 %>% val_labels
```
Then we calculate a table for each of the labels in `D4`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(D4, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D4) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$D4 %>% val_labels %>% names
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(D4, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D4) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
lapply(p.out, barplotfun)
```


---

### By empirical research engagement
First, we grab the info from `D5`
```{r}
raw_data$D5 %>% var_label
raw_data$D5 %>% val_labels
```
Then we calculate a table for each of the labels in `D5`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(D5, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D5) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$D5 %>% val_labels %>% names
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(D5, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(D5) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
lapply(p.out, barplotfun)
```

---

### By institutional support
First, we grab the info from `Group`
```{r}
raw_data$Group %>% var_label
raw_data$Group %>% val_labels
```
Then we calculate a table for each of the labels in `Group`
```{r}
out <- mice::complete(imp, 1) %>% 
  select(Group, all_of(QRP_set)) %>%
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(Group) %>% 
  group_map(~sapply(., table, simplify = TRUE))
names(out) <- raw_data$Group %>% val_labels %>% names
out
```
Then we calculate the proportional table
```{r}
p.out <- mice::complete(imp, 1) %>% 
  select(Group, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  mutate(across(where(is.numeric), as.factor)) %>% 
  group_by(Group) %>% 
  group_map(~sapply(., p_tab, simplify = TRUE)) 
names(p.out) <- names(out)
p.out
```
And the plots
```{r}
lapply(p.out, barplotfun)
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT