---
title: "A4 Means and SD's of QRP"
author: "Gerko Vink"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptives
library(tibble)   # Dataframes on steroids
library(gtools)   # Useful tools
library(DT)       # HTML tables
```

---

# Load the data
```{r}
load(file = "../Workspaces/3. Data imputation.Rdata")
load(file = "../Workspaces/2. Data inspection.Rdata")
```

---

# QRP without `Not Applicable`'s
First, we create an indicator for all QRP
```{r}
QRP_set <- names(raw_data[86:107])[-c(1, 2, 4, 6, 9, 12, 15, 16, 17, 19, 21 )]
```


## Descriptives and plots

### Overall
First, we calculate the descriptive statistics
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(all_of(QRP_set)) %>% 
  na_if(0) %>% 
  describe() %>% .[, 2:5] %>% 
  print.data.frame()
```

Second, we create a pointrangeplot
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(all_of(QRP_set)) %>% 
  na_if(0) %>% 
  describe(fast = TRUE) %>% 
  rownames_to_column(var = "Practices") %>% 
  mutate(min = mean - 1.96*sd, # subtract [1.96] SD
         max = mean + 1.96*sd,
         Practices = reorder(Practices, mixedorder(Practices))) %>%  
  ggplot(aes(x = Practices, y = mean)) + 
  geom_pointrange(aes(ymin = min, ymax = max))
```

---

### By disciplinary field
First, we calculate the descriptive statistics
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(D2, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  melt(id.vars = "D2", variable.name = "Practices", value.name = "Response") %>% 
  group_by(D2, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>% 
  print.data.frame()
```

Second, we create a pointrangeplot
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(D2, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  melt(id.vars = "D2", variable.name = "Practices", value.name = "Response") %>% 
  group_by(D2, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>% 
  ggplot(aes(x = Practices, y = mean, 
             ymin = mean - 1.96*sd, 
             ymax = mean + 1.96*sd)) + 
  geom_pointrange(aes(group = D2, colour = D2), 
                  position = position_dodge(width = 1)) + 
  theme_minimal()
```

---

### By rank
First, we calculate the descriptive statistics
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(D3, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  melt(id.vars = "D3", variable.name = "Practices", value.name = "Response") %>% 
  group_by(D3, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>%    
  print.data.frame()
```

Second, we create a pointrangeplot
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(D3, all_of(QRP_set)) %>% 
  mutate(D3 = recode(D3, "PhD student or junior researcher" = "PhD|Junior", "Postdoctoral researcher, Assistant Professor, Physician Researcher or Lecturer Researcher" = "PostDoc|AssistProf|Researcher", "Associate Professor or Full Professor" = "AssocProf|FullProf")) %>% 
  na_if(0) %>% 
  melt(id.vars = "D3", variable.name = "Practices", value.name = "Response") %>% 
  group_by(D3, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>% 
  ggplot(aes(x = Practices, y = mean, 
             ymin = mean - 1.96*sd, 
             ymax = mean + 1.96*sd)) + 
  geom_pointrange(aes(group = D3, colour = D3), 
                  position = position_dodge(width = 1)) + 
  theme_minimal()
```

---

### By gender identification
First, we calculate the descriptive statistics
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(D4, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  melt(id.vars = "D4", variable.name = "Practices", value.name = "Response") %>% 
  group_by(D4, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>%    
  print.data.frame()
```

Second, we create a pointrangeplot
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(D4, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  melt(id.vars = "D4", variable.name = "Practices", value.name = "Response") %>% 
  group_by(D4, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>% 
  ggplot(aes(x = Practices, y = mean, 
             ymin = mean - 1.96*sd, 
             ymax = mean + 1.96*sd)) + 
  geom_pointrange(aes(group = D4, colour = D4), 
                  position = position_dodge(width = 1)) + 
  theme_minimal()
```

---

### By  empirical research engagement
First, we calculate the descriptive statistics
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(D5, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  melt(id.vars = "D5", variable.name = "Practices", value.name = "Response") %>% 
  group_by(D5, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>%    
  print.data.frame()
```

Second, we create a pointrangeplot
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(D5, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  melt(id.vars = "D5", variable.name = "Practices", value.name = "Response") %>% 
  group_by(D5, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>% 
  ggplot(aes(x = Practices, y = mean, 
             ymin = mean - 1.96*sd, 
             ymax = mean + 1.96*sd)) + 
  geom_pointrange(aes(group = D5, colour = D5), 
                  position = position_dodge(width = 1)) + 
  theme_minimal()
```

---

### By institutional support
First, we calculate the descriptive statistics
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(Group, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  melt(id.vars = "Group", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Group, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>%    
  print.data.frame()
```

Second, we create a pointrangeplot
```{r}
mice::complete(imp, 1) %>% #QRP has no missings -so use 1st imputed set
  select(Group, all_of(QRP_set)) %>% 
  na_if(0) %>% 
  melt(id.vars = "Group", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Group, Practices) %>% 
  summarise_all(list(mean = mean, sd = sd), na.rm = TRUE) %>% 
  ggplot(aes(x = Practices, y = mean, 
             ymin = mean - 1.96*sd, 
             ymax = mean + 1.96*sd)) + 
  geom_pointrange(aes(group = Group, colour = Group), 
                  position = position_dodge(width = 1)) + 
  theme_minimal()
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT