---
title: "A8 Prevalence of any F1 Fabrication or F2 Falsification"
author: "Gerko Vink"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>

---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(plyr)     # Data manipulation
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptives
library(tibble)   # Dataframes on steroids
library(gtools)   # Useful tools
library(DT)       # HTML tables
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../Workspaces/5. Preparation Imputed Datasets.Rdata")
```

# Randomized response sum scores function
The following function cf. Cruyff, M. J., Van Den Hout, A., & Van Der Heijden, P. G. (2008). [The analysis of randomized response sum score variables](https://doi.org/10.1111/j.1467-9868.2007.00624.x). Journal of the Royal Statistical Society: Series B (Statistical Methodology), 70(1), 21-30.
```{r}
RR2 <- function(df){
  df <- na.omit(df)
  y  <- df$Freq
  n  <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  Q <- P %x% P
  phat <- solve(Q) %*% pobs
  varp <- (n - 1)^-1 * solve(Q) %*% (diag(pobs) -  pobs %*% t(pobs)) %*% t(solve(Q))
  data.frame(df, phat = phat, min95 = phat - 1.96*sqrt(diag(varp)), max95 = phat + 1.96*sqrt(diag(varp)))
}
```

---

## Prevalence

---

### Overall
We calculate the prevalence of any Falsification or Fabrication as
```{r}
d50[[1]] %$% 
  table(RRfals, RRfabr) %>% 
  melt(value.name = "Freq") %>% 
  RR2()
```

---

### By disciplinary field
We calculate the prevalence of any Falsification or Fabrication as
```{r}
d50[[1]] %$% 
  table(RRfals, RRfabr, Field) %>% 
  alply(3, .dims = TRUE) %>% 
  map(~ .x %>% 
        melt(value.name = "Freq") %>% 
        RR2)
```

---

### By rank
We calculate the prevalence of any Falsification or Fabrication as
```{r}
d50[[1]] %$% 
  table(RRfals, RRfabr, Rank) %>% 
  alply(3, .dims = TRUE) %>% 
  map(~ .x %>% 
        melt(value.name = "Freq") %>% 
        RR2)
```


---

### By gender identification
We calculate the prevalence of any Falsification or Fabrication as
```{r}
d50[[1]] %$% 
  table(RRfals, RRfabr, Gender) %>% 
  alply(3, .dims = TRUE) %>% 
  map(~ .x %>% 
        melt(value.name = "Freq") %>% 
        RR2)
```


---

### By  empirical research engagement
We calculate the prevalence of any Falsification or Fabrication as
```{r}
d50[[1]] %$% 
  table(RRfals, RRfabr, Research) %>% 
  alply(3, .dims = TRUE) %>% 
  map(~ .x %>% 
        melt(value.name = "Freq") %>% 
        RR2)
```


---

### By institutional support
We calculate the prevalence of any Falsification or Fabrication as
```{r}
d50[[1]] %$% 
  table(RRfals, RRfabr, Support) %>% 
  alply(3, .dims = TRUE) %>% 
  map(~ .x %>% 
        melt(value.name = "Freq") %>% 
        RR2)
```


---

# Session Info
```{r}
sessionInfo()
```
 
---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT


