---
title: "A9 Prevalence of F1 Fabrication"
author: "Gerko Vink"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>

---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptives
library(tibble)   # Dataframes on steroids
library(gtools)   # Useful tools
library(DT)       # HTML tables
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../Workspaces/3. Data imputation.Rdata")
load(file = "../Workspaces/2. Data inspection.Rdata")
load(file = "../Workspaces/5. Preparation Imputed Datasets.Rdata")
source(file = "../Functions/RR_functions.R")
```

---

## Prevalence

---

### Overall
We calculate the prevalence of any Fabrication as
```{r}
# Use RRreg::RRuni
raw_data %$% #F1 has no missings - so use first imputed set
  RRuni(RR1 - 1, model = "Warner", p = 5/6) #-1 because RRuni needs vector of 0 and 1 - not 1 and 2

# Custom function
RResp <- function(input, prob){
  yes <- input %>% table %>% prop.table %>% .[1]
  true <- (yes + prob - 1) / (2 * prob - 1)
  return(true)
}

RResp(raw_data$RR1, prob = 1/6)

table(raw_data$RR1)

#check
d50[[1]] %$% 
  table(RRfabr) %>% 
  melt(value.name = "Freq") %>% 
  RR1()

#double check
d50[[38]] %$% 
  table(RRfabr) %>% 
  melt(value.name = "Freq") %>% 
  RR1()
```

---

### By disciplinary field
We calculate the prevalence of any Fabrication as
```{r}
d50[[1]] %>% #F1 has no missings - so use first imputed set
  group_by(Field) %>% 
  summarise(true_proportion = RResp(RRfabr, prob = 1/6)) 

d50[[1]] %>% 
  group_by(Field) %>% 
  group_map(~.x %$% 
              RRuni(RRfabr, model = "Warner", p = 5/6))
  

d50[[1]] %>% #F1 has no missings - so use first imputed set
  filter(Field == "Soc & Beh") %$% 
  RResp(RRfabr, prob = 1/6)

d50[[1]] %>% #F1 has no missings - so use first imputed set
  filter(Field == "Arts & Hum") %$% 
  RResp(RRfabr, prob = 1/6)

d50[[1]] %>% #F1 has no missings - so use first imputed set
  filter(Field == "Eng & Nat") %$% 
  RResp(RRfabr, prob = 1/6)

d50[[1]] %>% #F1 has no missings - so use first imputed set
  filter(Field == "Bio & Life") %$% 
  RResp(RRfabr, prob = 1/6)

d50[[1]] %>% #F1 has no missings - so use first imputed set
  group_by(Field) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(RR1)
```

---

### By rank
We calculate the prevalence of any Fabrication as
```{r}
d50[[1]] %>% #F1 has no missings - so use first imputed set
  group_by(Rank) %>% 
  summarise(true_proportion = RResp(RRfabr, prob = 1/6)) 
```

---

### By gender identification
We calculate the prevalence of any Fabrication as
```{r}
d50[[1]] %>% #F1 has no missings - so use first imputed set
  group_by(Gender) %>% 
  summarise(true_proportion = RResp(RRfabr, prob = 1/6)) 
```
---

### By  empirical research engagement
We calculate the prevalence of any Fabrication as
```{r}
d50[[1]] %>% #F1 has no missings - so use first imputed set
  group_by(Research) %>% 
  summarise(true_proportion = RResp(RRfabr, prob = 1/6)) 
```

---

### By institutional support
We calculate the prevalence of any Fabrication as
```{r}
d50[[1]] %>% #F1 has no missings - so use first imputed set
  group_by(Support) %>% 
  summarise(true_proportion = RResp(RRfabr, prob = 1/6)) 
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT


