---
title: "B3 - Field by Rank by (non)Supporting institution"
author: "Gerko Vink"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
```

---

# Load the data
```{r}
load(file = "../Workspaces/5. Preparation Imputed Datasets.Rdata")
```

---

# Disciplinary field
The absolute frequencies for `Field` are
```{r}
d50[[1]] %$% # Take the first listed dimension because Field does not differ
  table(Field) 
```

The relative frequencies for `Field` are
```{r}
d50[[1]] %$% # Take the first listed dimension because Field does not differ
  table(Field) %>% 
  prop.table() %>% 
  round(3)
```

---

# Academic rank
The absolute frequencies for `Rank` are
```{r}
d50[[1]] %$% # Take the first listed dimension because Rank does not differ
  table(Rank) 
```

The relative frequencies for `Rank` are
```{r}
d50[[1]] %$% # Take the first listed dimension because Rank does not differ
  table(Rank) %>% 
  prop.table() %>% 
  round(3)
```

---

# Supporting institution
The absolute frequencies for `Support` are
```{r}
d50[[1]] %$% # Take the first listed dimension because Support does not differ
  table(Support) 
```

The relative frequencies for `Support` are
```{r}
d50[[1]] %$% # Take the first listed dimension because Support does not differ
  table(Support) %>% 
  prop.table() %>% 
  round(3)
```

---

# Field x Rank x Support
The absolute frequencies for Field x Rank x Support are
```{r}
d50[[1]] %$% # Take the first listed dimension because Gender does not differ
  table(Field, Rank, Support) 
```

The relative frequencies for Field x Rank x Support are
```{r}
d50[[1]] %$% # Take the first listed dimension because Gender does not differ
  table(Field, Rank, Support)  %>% 
  prop.table() %>% 
  round(3)
```

The plot of Field x Rank x Support
```{r}
d50[[1]] %$% # Take the first listed dimension because Gender does not differ
  table(Field, Rank, Support) %>% 
  as.data.frame() %>% 
  mutate(FieldSupp = paste(Field, Support)) %>% 
  ggplot(aes(x = FieldSupp, y = Freq, fill = Rank)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90))
```

and the plot of Rank x Field x Support
```{r}
d50[[1]] %$% # Take the first listed dimension because Gender does not differ
  table(Field, Rank, Support) %>% 
  as.data.frame() %>% 
  mutate(FieldSupp = paste(Field, Support)) %>% 
  ggplot(aes(x = Rank, y = Freq, fill = FieldSupp)) +
    geom_bar(stat = "identity")
```
 
---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT