---
title: "Table 1"
author: "Gerko Vink"
date: Characteristics of respondents by background variables and by the 10 explanatory
  variable scales
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(tibble)   # Tibbles
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
```

---

# Female
```{r echo = FALSE}
# Gender
r1a <- d50[[1]] %$% table(Gender, Field)[, c(4, 1, 3, 2)]
r1b <- d50[[1]] %$% table(Gender, Rank)
Overall <- d50[[1]] %$% table(Gender)
r2a <- d50[[1]] %$% table(Gender, Field) %>% prop.table(margin = 2) %>% .[2, c(4, 1, 3, 2)]*100 
r2b <- d50[[1]] %$% table(Gender, Rank) %>% prop.table(margin = 2) %>% .[2, c(1:3)]*100 
r2c <- d50[[1]] %$% table(Gender) %>% prop.table %>% .[2]
Row1 <- rbind(cbind(r1a, r1b, Overall), paste0("(", round(c(r2a, r2b, r2c), 3),")"))
rownames(Row1) <- c("Undisclosed N", "Female N", "Male N", "Female %")
# Research
r1a <- d50[[1]] %$% table(Research, Field)["Yes", c(4, 1, 3, 2)]
r1b <- d50[[1]] %$% table(Research, Rank)["Yes",]
r1c <- d50[[1]] %$% table(Research)["Yes"]
r2a <- d50[[1]] %$% table(Research, Field) %>% prop.table(margin = 2) %>% .["Yes", c(4, 1, 3, 2)]*100 
r2b <- d50[[1]] %$% table(Research, Rank) %>% prop.table(margin = 2) %>% .["Yes",]*100 
r2c <- d50[[1]] %$% table(Research) %>% prop.table %>% .["Yes"]*100  
Row2 <- rbind(c(r1a, r1b, r1c), paste0("(", round(c(r2a, r2b, r2c), 3),")"))
rownames(Row2) <- c("Empirical N", "Empirical %")
# Support
r1a <- d50[[1]] %$% table(Support, Field)["Yes", c(4, 1, 3, 2)]
r1b <- d50[[1]] %$% table(Support, Rank)["Yes",]
r1c <- d50[[1]] %$% table(Support)["Yes"]
r2a <- d50[[1]] %$% table(Support, Field) %>% prop.table(margin = 2) %>% .["Yes", c(4, 1, 3, 2)]*100 
r2b <- d50[[1]] %$% table(Support, Rank) %>% prop.table(margin = 2) %>% .["Yes",]*100 
r2c <- d50[[1]] %$% table(Support) %>% prop.table %>% .["Yes"]*100  
Row3 <- rbind(c(r1a, r1b, r1c), paste0("(", round(c(r2a, r2b, r2c), 3),")"))
rownames(Row3) <- c("Support N", "Support %")
# Means
evs  <- c("SciNorms", "PeerNorms", "WorkPress", "PubPress", "FundPress",
         "Competitive","DetectCol", "DetectRev", "Mentoring", "OrgJust")
#Overall
Overall <- rbind(
  d50 %>% map(select, SciNorms) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50,
d50 %>% map(select, PeerNorms) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50,
d50 %>% map(select, WorkPress) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50,
d50 %>% map(select, PubPress) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50,
d50 %>% map(select, FundPress) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50,
d50 %>% map(select, Competitive) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50,
d50 %>% map(select, DetectCol) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50,
d50 %>% map(select, DetectRev) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50,
d50 %>% map(select, Mentoring) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50,
d50 %>% map(select, OrgJust) %>% 
  map(~.x %>% mean_cl_normal %>% round(4)) %>% 
  Reduce("+", .) / 50) 
Overall %<>% 
  mutate(ci = paste("(", ymin, ",", ymax, ")", sep = ""))
rownames(Overall) <- evs
m.overall <- Overall$y
ci.overall <- Overall$ci
#biomed
bio <- rbind(
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(SciNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(PeerNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(WorkPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(PubPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(FundPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(Competitive) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(DetectCol) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(DetectRev) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(Mentoring) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Bio & Life") %>% 
              select(OrgJust) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50) %>% 
  round(3) %>% 
  mutate(ci = paste("(", ymin, ",", ymax, ")", sep = ""))
rownames(bio) <- evs
m.bio <- bio$y
ci.bio <- bio$ci




#socialmed
social <- rbind(
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(SciNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(PeerNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(WorkPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(PubPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(FundPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(Competitive) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(DetectCol) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(DetectRev) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(Mentoring) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Soc & Beh") %>% 
              select(OrgJust) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50) %>% 
  round(3) %>% 
  mutate(ci = paste("(", ymin, ",", ymax, ")", sep = ""))
rownames(social) <- evs
m.social <- social$y
ci.social <- social$ci



#artshummed
artshum <- rbind(
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(SciNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(PeerNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(WorkPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(PubPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(FundPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(Competitive) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(DetectCol) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(DetectRev) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(Mentoring) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Arts & Hum") %>% 
              select(OrgJust) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50) %>% 
  round(3) %>% 
  mutate(ci = paste("(", ymin, ",", ymax, ")", sep = ""))
rownames(artshum) <- evs
m.artshum <- artshum$y
ci.artshum <- artshum$ci





#Eng & Nat
engnat <- rbind(
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(SciNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(PeerNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(WorkPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(PubPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(FundPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(Competitive) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(DetectCol) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(DetectRev) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(Mentoring) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Field == "Eng & Nat") %>% 
              select(OrgJust) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50) %>% 
  round(3) %>% 
  mutate(ci = paste("(", ymin, ",", ymax, ")", sep = ""))
rownames(engnat) <- evs
m.engnat <- engnat$y
ci.engnat <- engnat$ci


#Phd
phd <- rbind(
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(SciNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(PeerNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(WorkPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(PubPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(FundPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(Competitive) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(DetectCol) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(DetectRev) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(Mentoring) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "PhD") %>% 
              select(OrgJust) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50) %>% 
  round(3) %>% 
  mutate(ci = paste("(", ymin, ",", ymax, ")", sep = ""))
rownames(phd) <- evs
m.phd <- phd$y
ci.phd <- phd$ci




#Postdoc
postdoc <- rbind(
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(SciNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(PeerNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(WorkPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(PubPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(FundPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(Competitive) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(DetectCol) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(DetectRev) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(Mentoring) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Postdoc") %>% 
              select(OrgJust) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50) %>% 
  round(3) %>% 
  mutate(ci = paste("(", ymin, ",", ymax, ")", sep = ""))
rownames(postdoc) <- evs
m.postdoc <- postdoc$y
ci.postdoc <- postdoc$ci

#Prof
prof <- rbind(
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(SciNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(PeerNorms) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(WorkPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(PubPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(FundPress) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(Competitive) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(DetectCol) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(DetectRev) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(Mentoring) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50,
d50 %>% map(~.x %>% 
              filter(Rank == "Prof") %>% 
              select(OrgJust) %>% 
              
              mean_cl_normal()) %>% 
  Reduce("+", .) / 50) %>% 
  round(3) %>% 
  mutate(ci = paste("(", ymin, ",", ymax, ")", sep = ""))
rownames(prof) <- evs
m.prof <- prof$y
ci.prof <- prof$ci

MeanCI <- cbind(
c(rbind(m.bio, ci.bio)),
c(rbind(m.social, ci.social)),
c(rbind(m.engnat, ci.engnat)),
c(rbind(m.artshum, ci.artshum)),
c(rbind(m.phd, ci.phd)),
c(rbind(m.postdoc, ci.postdoc)),
c(rbind(m.prof, ci.prof)), 
c(rbind(m.overall, ci.overall))
)
rownames(MeanCI) <- c(rbind(paste(evs, "MEAN", sep = "_"),
                            paste(evs, "CI", sep = "_")))

options(DT.options = list(pageLength = 50))
rbind(Row1, Row2, Row3, MeanCI) %>% 
  datatable(options = )

rbind(Row1, Row2, Row3, MeanCI) %>% 
  as.data.frame()
```


---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT