---
title: "Fig2 - Barchart - Overall QRP"
author: "Gerko Vink"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(gridExtra)# Grids
library(tidyr)    # Tidy modeling
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
```

---

# Plot with Not Applicable
```{r}
d <- d50[[1]] %>% #RRP has no missings -so use 1st imputed set
  select(starts_with("Q"))
names(d) <- paste("QRP", 1:11, sep = "")
a <- d %>% 
  select(1:11) %>% 
  sapply(table) %>% 
  melt(varnames = c("Response", "Practices")) %>% 
  mutate(Response = factor(Response),
         Percentage = value / (sum(value)/11),
         Response = recode(Response, `0` = "Not Applicable", `1` = "1 Never", `7` = "7 Always")) %>% 
  ggplot(aes(x = Practices, y = Percentage, fill = Response)) +
  geom_bar(stat = 'identity', position = "stack", colour="black") +
  geom_col(position = position_stack(reverse = TRUE)) + 
  scale_fill_brewer(palette = "RdBu", direction = -1) +
  scale_y_continuous(labels = scales::percent) + 
  theme_minimal()  + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_manual(values = rev(c("#D6604D", "#F4A582", "#FDDBC7", "#D1E5F0", "#92C5DE", "#4393C3", "#2166AC", "grey50"))) + 
  guides(fill = guide_legend(reverse = TRUE))
a
pdf(file = "Fig2_withNA.pdf", width = 10, height = 6)
a
dev.off()

pdf(file = "Fig2_withNA_large.pdf", width = 6, height = 4)
a
dev.off()
```

--

# Plot without Not Applicable
```{r}
d <- d50[[1]] %>% #RRP has no missings -so use 1st imputed set
  select(starts_with("Q")) %>% 
  select(!contains("_"))
names(d) <- paste("QRP", 1:11, sep = "")
p <- d %>% 
  sapply(table) %>% 
  melt(varnames = c("Response", "Practices")) %>% 
  mutate(Response = factor(Response),
         Percentage = value / (sum(value)/11),
         Response = recode(Response, `0` = "Not Applicable", `1` = "1 Never", `7` = "7 Always")) %>% 
  ggplot(aes(x = Practices, y = Percentage, fill = Response)) +
  geom_bar(stat = 'identity', position = "stack", colour="black") +
  geom_col(position = position_stack(reverse = TRUE)) + 
  scale_fill_brewer(palette = "RdBu", direction = -1) +
  scale_y_continuous(labels = scales::percent) + 
  theme_minimal()  + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))  +
  scale_fill_manual(values = rev(c("#B2182B", "#D6604D", "#F4A582", "#FDDBC7", "#D1E5F0", "#92C5DE", "#4393C3", "#2166AC"))) + 
  guides(fill = guide_legend(reverse = TRUE))

p
pdf(file = "Fig2.pdf", width = 10, height = 6)
p
dev.off()

pdf(file = "Fig2_large.pdf", width = 6, height = 3.5)
p
dev.off()

```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT