---
title: "Table 2"
author: "Gerko Vink"
date: Mean score and prevalence^^  of Questionable Research Practices (QRP), Falsification, and Fabrication stratified by Disciplinary Gender, Research and Research
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptive tables
library(tibble)   # Tibbles
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
options(DT.options = list(pageLength = 50)) # table options
```

```{r echo = FALSE}
## RR functions
RR2 <- function(df){
  df <- na.omit(df)
  y  <- df$Freq
  n  <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  Q <- P %x% P
  phat <- solve(Q) %*% pobs
  varp <- (n - 1)^-1 * solve(Q) %*% (diag(pobs) -  pobs %*% t(pobs)) %*% t(solve(Q))
  min95 <- phat - 1.96*sqrt(diag(varp))
  max95 <- phat + 1.96*sqrt(diag(varp))
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat, 3), paste("(", round(min95, 3), ",", round(max95, 3), ")", sep = "")))
}

RR1 <- function(df){
  y <- df$Freq
  n <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  phat <- solve(P) %*% pobs
  varp <- prod(pobs)/(n*(P[2,2]-P[2,1])^2)
  min95 <- phat - 1.96*sqrt(varp)
  max95 <- phat + 1.96*sqrt(varp)
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat, 3), paste("(", round(min95, 3), ",", round(max95, 3), ")", sep = "")))
}
```

---

# Means
```{r echo = FALSE}
Support <- d50[[1]] %>% 
  select(contains("Q"), Support) %>% # select relevant columns
  select(!contains("_"), Support) %>% # exclude raw
  melt(id.vars = "Support", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Support, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 2), ",", round(upr, 2), ")", sep = ""),
         mean = round(mean, 3),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, mean, ci, m.ci) 

mci.Support <- Support %>% dcast(Practices ~ Support, value.var = "m.ci") %>% 
  rename(`Support (Yes)` = Yes, `Support (No)` = No)
```
```{r echo = FALSE}
Gender <- d50[[1]] %>% 
  select(contains("Q"), Gender) %>% # select relevant columns
  select(!contains("_"), Gender) %>% # exclude raw
  melt(id.vars = "Gender", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Gender, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 2), ",", round(upr, 2), ")", sep = ""),
         mean = round(mean, 3),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, Gender, mean, ci, m.ci) 

mci.Gender <- Gender %>% dcast(Practices ~ Gender, value.var = "m.ci") %>% .[, c(1, 4, 3, 2)]
```

```{r echo = FALSE}
Research <- d50[[1]] %>% 
  select(contains("Q"), Research) %>% # select relevant columns
  select(!contains("_"), Research) %>% # exclude raw
  melt(id.vars = "Research", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Research, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 2), ",", round(upr, 2), ")", sep = ""),
         mean = round(mean, 3)) %>% 
  select(Practices, Research, mean, ci) 

mci.Research <- Research %>% mutate(m.ci = paste(mean, ci, sep = " ")) %>% dcast(Practices ~ Research, value.var = "m.ci") %>% 
  rename(`Research (Yes)` = Yes, `Research (No)` = No)
```

```{r echo = FALSE}
Means <- merge(mci.Gender, mci.Research, by.x = "Practices")
Means <- merge(Means, mci.Support, by.x = "Practices")

datatable(Means)
Means
```

---

# Prevalence of QRP items
```{r echo = FALSE}
p.test <- function(x){
  t <- suppressWarnings(prop.test(x))
  paste(round(t$estimate, 3),
        paste("(", round(t$conf.int[1], 3), ",", round(t$conf.int[2], 3), ")", sep = ""))
}
p.fun <- function(x){
  if(sum(x > 4) == 0) {
    return("none")
    } else {
  table(x > 4) %>% .[c(2, 1)] %>% t() %>% p.test
  }
}

Prevalence_QRP_Support <- d50[[1]] %>% 
  select(contains("Q"), Support) %>% # select relevant columns
  select(!contains("_"), Support) %>%
  group_by(Support) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[-1, ] %>% 
  as.data.frame() %>% 
  `colnames<-`(names(Means)[7:8])
  
Prevalence_QRP_Gender <- d50[[1]] %>% 
  select(contains("Q"), Gender) %>% # select relevant columns
  select(!contains("_"), Gender) %>%
  group_by(Gender) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t()  %>% 
  .[-1, 3:1] %>% as.data.frame() %>% 
  `colnames<-`(names(Means)[2:4])

Prevalence_QRP_Research <- d50[[1]] %>% 
  select(contains("Q"), Research) %>% # select relevant columns
  select(!contains("_"), Research) %>%
  group_by(Research) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[-1, ] %>% 
  as.data.frame() %>% 
  `colnames<-`(names(Means)[5:6])

prevalence <- cbind(Prevalence_QRP_Gender, 
                    Prevalence_QRP_Research, 
                    Prevalence_QRP_Support) %>% 
  .[c(1, 6, 8, 10, 9, 3, 7, 11, 2, 4, 5), ] #correct row order
prevalence %>% datatable()
prevalence
```

---

# Prevalence of any QRP and Randomized Response
```{r echo=FALSE}
QRP1_Gender <- d50[[1]] %>% 
  select(Gender, QRP_1) %>% 
  group_by(Gender) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") %>% 
  .[, 4:1] #reorder, cf. table
Fals_Gender <- d50[[1]] %>% 
  group_by(Gender) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") %>% 
  .[, 4:1] #reorder, cf. table
Fabr_Gender <- d50[[1]] %>% 
  group_by(Gender) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") %>% 
  .[, 4:1] #reorder, cf. table
FF_Gender <- d50[[1]] %>% 
  group_by(Gender) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "FF") %>% 
  .[, 4:1] #reorder, cf. table

prev.Gender <- rbind(QRP1_Gender, Fals_Gender, Fabr_Gender, FF_Gender)
colnames(prev.Gender)[2:4] <- names(Means)[2:4]
```

```{r echo=FALSE}
QRP1_Research <- d50[[1]] %>% 
  select(Research, QRP_1) %>% 
  group_by(Research) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") 
Fals_Research <- d50[[1]] %>% 
  group_by(Research) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") 
Fabr_Research <- d50[[1]] %>% 
  group_by(Research) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") 
FF_Research <- d50[[1]] %>% 
  group_by(Research) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% round(3) %>% 
  mutate(Indicator = "FF") 

prev.Research <- rbind(QRP1_Research, Fals_Research, Fabr_Research, FF_Research)[, c(3, 1, 2)]
colnames(prev.Research)[2:3] <- names(Means)[5:6]
```

```{r echo=FALSE}
QRP1_Support <- d50[[1]] %>% 
  select(Support, QRP_1) %>% 
  group_by(Support) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") 
Fals_Support <- d50[[1]] %>% 
  group_by(Support) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") 
Fabr_Support <- d50[[1]] %>% 
  group_by(Support) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") 
FF_Support <- d50[[1]] %>% 
  group_by(Support) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% round(3) %>% 
  mutate(Indicator = "FF") 

prev.Support <- rbind(QRP1_Support, Fals_Support, Fabr_Support, FF_Support)[, c(3, 1, 2)]
colnames(prev.Support)[2:3] <- names(Means)[7:8]
```

```{r}
prevalence <- merge(prev.Gender, prev.Research, by.x = "Indicator")
merge(prevalence, prev.Support, by.x = "Indicator") %>% 
  datatable()
merge(prevalence, prev.Support, by.x = "Indicator")
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT