---
title: "Table 2"
author: "Gerko Vink"
date: Mean score and prevalence^^  of Questionable Research Practices (QRP), Falsification, and Fabrication stratified by Disciplinary Gender, Research and Research without NA
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptive tables
library(tibble)   # Tibbles
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
options(DT.options = list(pageLength = 50)) # table options
```

```{r echo = FALSE}
## RR functions
RR2 <- function(df){
  df <- na.omit(df)
  y  <- df$Freq
  n  <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  Q <- P %x% P
  phat <- solve(Q) %*% pobs
  varp <- (n - 1)^-1 * solve(Q) %*% (diag(pobs) -  pobs %*% t(pobs)) %*% t(solve(Q))
  min95 <- phat - 1.96*sqrt(diag(varp))
  max95 <- phat + 1.96*sqrt(diag(varp))
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat, 3), paste("(", round(min95, 3), ",", round(max95, 3), ")", sep = "")))
}

RR1 <- function(df){
  y <- df$Freq
  n <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  phat <- solve(P) %*% pobs
  varp <- prod(pobs)/(n*(P[2,2]-P[2,1])^2)
  min95 <- phat - 1.96*sqrt(varp)
  max95 <- phat + 1.96*sqrt(varp)
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat, 3), paste("(", round(min95, 3), ",", round(max95, 3), ")", sep = "")))
}
```

---

# Means
```{r echo = FALSE}
qrp <- c("QAttention", "QSupervision", "QResDesign", "QUnfairRev", "QUnsubstClaims", 
         "QCiteSource", "QResNotes", "QConcealDetails", "QNoReSubmit", "QConcealFlaws", "QSelectCites")

Q <- d50
Q <- Q %>% 
  map(~ .x %>% 
        mutate_at(paste(qrp, "_raw", sep = ""), ~ na_if(., 0))) %>% 
  map(~.x %>% 
        mutate(QRPave = rowMeans(select(., 92:102), na.rm = FALSE)))
meangv <- function(x){mean(x, na.rm = TRUE)}
sdgv <- function(x){sd(x, na.rm = TRUE)}

Support <- Q[[1]] %>% 
  select(contains("Q"), Support) %>% # select relevant columns
  select(contains("raw"), Support) %>% # select raw
  melt(id.vars = "Support", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Support, Practices) %>% 
  summarise_all(list(n = length, mean = meangv, sd = sdgv)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, mean, ci, m.ci) 

mci.Support <- Support %>% dcast(Practices ~ Support, value.var = "m.ci") %>% 
  rename(`Support (Yes)` = Yes, `Support (No)` = No)
```
```{r echo = FALSE}
Gender <- Q[[1]] %>% 
  select(contains("Q"), Gender) %>% # select relevant columns
  select(contains("raw"), Gender) %>% # select raw
  melt(id.vars = "Gender", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Gender, Practices) %>% 
  summarise_all(list(n = length, mean = meangv, sd = sdgv)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, Gender, mean, ci, m.ci) 

mci.Gender <- Gender %>% dcast(Practices ~ Gender, value.var = "m.ci") %>% .[, c(1, 4, 3, 2)]
```

```{r echo = FALSE}
Research <- Q[[1]] %>% 
  select(contains("Q"), Research) %>% # select relevant columns
  select(contains("raw"), Research) %>% # select raw
  melt(id.vars = "Research", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Research, Practices) %>% 
  summarise_all(list(n = length, mean = meangv, sd = sdgv)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1)) %>% 
  select(Practices, Research, mean, ci) 

mci.Research <- Research %>% mutate(m.ci = paste(mean, ci, sep = " ")) %>% dcast(Practices ~ Research, value.var = "m.ci") %>% 
  rename(`Research (Yes)` = Yes, `Research (No)` = No)
```

```{r echo = FALSE}
Means <- merge(mci.Gender, mci.Research, by.x = "Practices", sort = FALSE)
Means <- merge(Means, mci.Support, by.x = "Practices", sort = FALSE)
datatable(Means)
Means
```

---

# Prevalence of QRP items
```{r echo = FALSE}
p.test <- function(x){
  t <- suppressWarnings(prop.test(x))
  paste(round(t$estimate*100, 1),
        paste("(", round(t$conf.int[1]*100, 1), ",", round(t$conf.int[2]*100, 1), ")", sep = ""))
}
p.fun <- function(x){
  if(sum(x > 4, na.rm = TRUE) == 0) {
    return("none")
    } 
  if(dim(table(x > 4)) == 1){return("100")} else {
  table(x > 4) %>% .[c(2, 1)] %>% t() %>% p.test
  }
}

Prevalence_QRP_Support <- Q[[1]] %>% 
  select(contains("Q"), Support) %>% # select relevant columns
  select(contains("raw"), Support) %>%
  group_by(Support) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[-1, ] %>% 
  as.data.frame() %>% 
  `colnames<-`(names(Means)[7:8])
  
Prevalence_QRP_Gender <- Q[[1]] %>% 
  select(contains("Q"), Gender) %>% # select relevant columns
  select(contains("raw"), Gender) %>%
  group_by(Gender) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t()  %>% 
  .[-1, 3:1] %>% as.data.frame() %>% 
  `colnames<-`(names(Means)[2:4])

Prevalence_QRP_Research <- Q[[1]] %>% 
  select(contains("Q"), Research) %>% # select relevant columns
  select(contains("raw"), Research) %>%
  group_by(Research) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[-1, ] %>% 
  as.data.frame() %>% 
  `colnames<-`(names(Means)[5:6])

prevalence <- cbind(Prevalence_QRP_Gender, 
                    Prevalence_QRP_Research, 
                    Prevalence_QRP_Support) 
prevalence %>% datatable()
prevalence
```

```{r}
Out <- rbind(Means, prevalence %>% rownames_to_column(var = "Practices"))[c(1,12, 2, 13, 3, 14, 4, 15, 5, 16, 6, 17, 7, 18, 8, 19, 9, 20, 10, 21, 11, 22), ]
datatable(Out)
Out
write.table(Out[, -c(6, 8)], file = "SupplTable2_meanprevalence.txt", sep = "\t")
```


---

# Prevalence of any QRP and Randomized Response
```{r echo=FALSE}
QRP1_Gender <- d50[[1]] %>% 
  select(Gender, QRP_1) %>% 
  group_by(Gender) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") %>% 
  .[, 4:1] #reorder, cf. table
Fals_Gender <- d50[[1]] %>% 
  group_by(Gender) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") %>% 
  .[, 4:1] #reorder, cf. table
Fabr_Gender <- d50[[1]] %>% 
  group_by(Gender) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") %>% 
  .[, 4:1] #reorder, cf. table
FF_Gender <- d50[[1]] %>% 
  group_by(Gender) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "FF") %>% 
  .[, 4:1] #reorder, cf. table

prev.Gender <- rbind(QRP1_Gender, Fals_Gender, Fabr_Gender, FF_Gender)
colnames(prev.Gender)[2:4] <- names(Means)[2:4]
```

```{r echo=FALSE}
QRP1_Research <- d50[[1]] %>% 
  select(Research, QRP_1) %>% 
  group_by(Research) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") 
Fals_Research <- d50[[1]] %>% 
  group_by(Research) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") 
Fabr_Research <- d50[[1]] %>% 
  group_by(Research) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") 
FF_Research <- d50[[1]] %>% 
  group_by(Research) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% round(3) %>% 
  mutate(Indicator = "FF") 

prev.Research <- rbind(QRP1_Research, Fals_Research, Fabr_Research, FF_Research)[, c(3, 1, 2)]
colnames(prev.Research)[2:3] <- names(Means)[5:6]
```

```{r echo=FALSE}
QRP1_Support <- d50[[1]] %>% 
  select(Support, QRP_1) %>% 
  group_by(Support) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") 
Fals_Support <- d50[[1]] %>% 
  group_by(Support) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") 
Fabr_Support <- d50[[1]] %>% 
  group_by(Support) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") 
FF_Support <- d50[[1]] %>% 
  group_by(Support) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% round(3) %>% 
  mutate(Indicator = "FF") 

prev.Support <- rbind(QRP1_Support, Fals_Support, Fabr_Support, FF_Support)[, c(3, 1, 2)]
colnames(prev.Support)[2:3] <- names(Means)[7:8]
```

```{r}
prevalence <- merge(prev.Gender, prev.Research, by.x = "Indicator")
merge(prevalence, prev.Support, by.x = "Indicator") %>% 
  datatable()
merge(prevalence, prev.Support, by.x = "Indicator")
```


---

# Percentage of NA's over Field
The following table displays the percentage of Not Applicable per RRP over Field. RRPave shows the percentage of rows that have at least one RRP as NA.
```{r echo = FALSE}
sumna <- function(x){sum(is.na(x))}

Field <- Q[[1]] %>% 
  select(starts_with("Q"), Field) %>% 
  select(contains("raw"), QRPave, Field) %>%  # exclude raw
  melt(id.vars = "Field", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Field, Practices) %>% 
  summarise_all(list(n = length, sum = sumna)) %>% 
  mutate(perc = round(100*sum/n, 1)) %>% 
  select(Practices, Field, perc, sum, n) 

na.Field <- Field %>% dcast(Practices ~ Field, value.var = "perc") %>% .[, c(1, 5, 2, 4, 3)]
```

---

# Percentage of NA's over Rank
The following table displays the percentage of Not Applicable per RRP over Rank. QRPave shows the percentage of rows that have at least one RRP as NA.
```{r echo = FALSE}
sumna <- function(x){sum(is.na(x))}

Rank <- Q[[1]] %>% 
  select(starts_with("Q"), Rank) %>% 
  select(contains("raw"), QRPave, Rank) %>%  # exclude raw
  melt(id.vars = "Rank", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Rank, Practices) %>% 
  summarise_all(list(n = length, sum = sumna)) %>% 
  mutate(perc = round(100*sum/n, 1)) %>% 
  select(Practices, Rank, perc, sum, n) 

na.Rank <- Rank %>% dcast(Practices ~ Rank, value.var = "perc")
```

```{r}
p.FR <- cbind(na.Field, na.Rank[, -1])
datatable(p.FR)
p.FR
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT