---
title: "Table 1"
author: "Gerko Vink"
date: Characteristics of respondents by background variables and by the 10 explanatory
  variable scales
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(tibble)   # Tibbles
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
```


---

# Z-scores
```{r}
Z <- d50 %>% map(~.x %>% 
                   group_by(Field) %>% 
                   summarise(across(evs, ~ mean(.x, na.rm = TRUE))) %>% 
                   column_to_rownames("Field")) %>% 
  Reduce("+", .) / 50
round(Z, 2)
```

---

```{r alpha , eval = FALSE}
alpha <- bind_rows(
  d50 %>% map(select, F1:F9) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F10:F18) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F19:F21) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F22:F27) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F28:F33) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F40:F45) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F64:F69) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F70:F75) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F34:F39) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F46:F51) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used"),
  d50 %>% map(select, F52:F63) %>% 
    map(~alpha(.) %>% pluck("total") %>% pluck("std.alpha")) %>% as.data.frame %>%  
    mutate(alpha = rowMeans(.), .keep = "used")
)  
```

```{r eval = FALSE}
data.frame(alpha,
           row.names = evs) %>% round(2)
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT