---
title: "Table 2"
author: "Gerko Vink"
date: Mean score and prevalence^^  of Questionable Research Practices (QRP), Falsification, and Fabrication stratified by Disciplinary Field and Academic Rank without NA's
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptive tables
library(tibble)   # Tibbles
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../../Workspaces/5. Preparation Imputed Datasets.Rdata")
options(DT.options = list(pageLength = 50)) # table options
```

```{r echo = FALSE}
## RR functions
RR2 <- function(df){
  df <- na.omit(df)
  y  <- df$Freq
  n  <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  Q <- P %x% P
  phat <- solve(Q) %*% pobs
  varp <- (n - 1)^-1 * solve(Q) %*% (diag(pobs) -  pobs %*% t(pobs)) %*% t(solve(Q))
  min95 <- phat - 1.96*sqrt(diag(varp))
  max95 <- phat + 1.96*sqrt(diag(varp))
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat*100, 1), paste("(", round(min95*100, 1), ",", round(max95*100, 1), ")", sep = "")))
}

RR1 <- function(df){
  y <- df$Freq
  n <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  phat <- solve(P) %*% pobs
  varp <- prod(pobs)/(n*(P[2,2]-P[2,1])^2)
  min95 <- phat - 1.96*sqrt(varp)
  max95 <- phat + 1.96*sqrt(varp)
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat*100, 1), paste("(", round(min95*100, 1), ",", round(max95*100, 1), ")", sep = "")))
}
```

---

# Means without NA's
```{r echo = FALSE}
qrp <- c("QAttention", "QSupervision", "QResDesign", "QUnfairRev", "QUnsubstClaims", 
         "QCiteSource", "QResNotes", "QConcealDetails", "QNoReSubmit", "QConcealFlaws", "QSelectCites")

Q <- d50
Q <- Q %>% 
  map(~ .x %>% 
        mutate_at(paste(qrp, "_raw", sep = ""), ~ na_if(., 0))) %>% 
  map(~.x %>% 
        mutate(QRPave = rowMeans(select(., 92:102), na.rm = FALSE)))
meangv <- function(x){mean(x, na.rm = TRUE)}
sdgv <- function(x){sd(x, na.rm = TRUE)}

Overall <- Q[[1]] %>% 
  select(contains("Q"), QRPave) %>% # select relevant columns
  select(contains("raw"), QRPave) %>% # exclude raw
  melt(variable.name = "Practices") %>% 
  group_by(Practices) %>% 
  summarise_all(list(n = length, mean = meangv, sd = sdgv)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, mean, ci, m.ci) 
mci.overall <- Overall %>% select(Practices, m.ci) %>% rename(Overall = m.ci)
```
```{r echo = FALSE}
Field <- Q[[1]] %>% 
  select(contains("Q"), QRPave,  Field) %>% # select relevant columns
  select(contains("raw"), QRPave, Field) %>% # exclude raw
  melt(id.vars = "Field", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Field, Practices) %>% 
  summarise_all(list(n = length, mean = meangv, sd = sdgv)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, Field, mean, ci, m.ci) 

mci.Field <- Field %>% dcast(Practices ~ Field, value.var = "m.ci") %>% .[, c(1, 5, 2, 4, 3)]
```

```{r echo = FALSE}
Rank <- Q[[1]] %>% 
  select(contains("Q"), QRPave, Rank) %>% # select relevant columns
  select(contains("raw"), QRPave, Rank) %>% # exclude raw
  melt(id.vars = "Rank", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Rank, Practices) %>% 
  summarise_all(list(n = length, mean = meangv, sd = sdgv)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 1), ",", round(upr, 1), ")", sep = ""),
         mean = round(mean, 1)) %>% 
  select(Practices, Rank, mean, ci) 

mci.Rank <- Rank %>% mutate(m.ci = paste(mean, ci, sep = " ")) %>% dcast(Practices ~ Rank, value.var = "m.ci")
```

```{r echo = FALSE}
Means <- merge(mci.Field, mci.Rank, by.x = "Practices")
Means <- merge(Means, mci.overall, by.x = "Practices")
Means <- Means[c(1, 10, 6, 11, 12, 2, 7, 3, 5, 4, 9, 8), ]
datatable(Means)
Means
```

---

# Prevalence of QRP items
```{r echo = FALSE}
p.test <- function(x){
  t <- suppressWarnings(prop.test(x))
  paste(round(t$estimate*100, 1),
        paste("(", round(t$conf.int[1]*100, 1), ",", round(t$conf.int[2]*100, 1), ")", sep = ""))
}
p.fun <- function(x){
  if(sum(x > 4, na.rm = TRUE) == 0) {
    return("none")
    } 
  if(dim(table(x > 4)) == 1){return("100")} else {
  table(x > 4) %>% .[c(2, 1)] %>% t() %>% p.test
  }
}
Prevalence_QRP_Overall <- Q[[1]] %>% 
  select(contains("Q")) %>% # select relevant columns
  select(contains("raw")) %>%
  summarise_all(list(prevalence = p.fun)) %>% t() %>% 
  data.frame(Overall = .)

Prevalence_QRP_Field <- Q[[1]] %>% 
  select(contains("Q"), Field) %>% # select relevant columns
  select(contains("raw"), Field) %>%
  group_by(Field) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[, c(4, 1, 3, 2)] %>% 
  .[-1, ] %>% as.data.frame() %>% 
  `colnames<-`(names(Means)[2:5])

Prevalence_QRP_Rank <- Q[[1]] %>% 
  select(contains("Q"), Rank) %>% # select relevant columns
  select(contains("raw"), Rank) %>%
  group_by(Rank) %>% 
  summarise_all(list(prevalence = p.fun)) %>% t() %>% .[-1, ] %>% 
  as.data.frame() %>% 
  `colnames<-`(names(Means)[6:8])

prevalence <- cbind(Prevalence_QRP_Field, 
                    Prevalence_QRP_Rank, 
                    Prevalence_QRP_Overall) #correct row order
prevalence %>% datatable()
prevalence
```

---

# Prevalence of any QRP and Randomized Response
```{r echo = FALSE}
p.test <- function(x){
  t <- suppressWarnings(prop.test(x))
  paste(round(t$estimate*100, 1),
        paste("(", round(t$conf.int[1]*100, 1), ",", round(t$conf.int[2]*100, 1), ")", sep = ""))
}
p.fun <- function(x){
  table(x > 4) %>% .[c(2, 1)] %>% t() %>% p.test
}
QRP1_overall <- d50[[1]] %$% #QRP has no missings -so use 1st imputed set
  table(1 - QRP_1)  %>% p.test
Fals_overall <- d50[[1]] %$% 
  table(RRfals) %>% 
  melt(value.name = "Freq") %>% 
  RR1() %>%  .$p.ci %>% .[2]
Fabr_overall <- d50[[1]] %$% 
  table(RRfabr) %>% 
  melt(value.name = "Freq") %>% 
  RR1() %>%  .$p.ci %>% .[2]
FF_overall <- d50[[1]] %$% 
  table(RRfals, RRfabr) %>% 
  melt(value.name = "Freq") %>% 
  RR2() %>% .$phat %>% .[2:4] %>% sum 

prev.overall <- data.frame(Overall = c(QRP1_overall, Fals_overall, Fabr_overall, round(FF_overall, 1)))
```
```{r echo=FALSE}
QRP1_Field <- d50[[1]] %>% 
  select(Field, QRP_1) %>% 
  group_by(Field) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") %>% 
  .[, c(5, 4, 1, 3, 2)] #reorder, cf. table
Fals_Field <- d50[[1]] %>% 
  group_by(Field) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") %>% 
  .[, c(5, 4, 1, 3, 2)] #reorder, cf. table
Fabr_Field <- d50[[1]] %>% 
  group_by(Field) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") %>% 
  .[, c(5, 4, 1, 3, 2)] #reorder, cf. table
FF_Field <- d50[[1]] %>% 
  group_by(Field) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "FF") %>% 
  .[, c(5, 4, 1, 3, 2)] #reorder, cf. table

prev.Field <- rbind(QRP1_Field, Fals_Field, Fabr_Field, FF_Field)
colnames(prev.Field)[2:5] <- names(Means)[2:5]
```
```{r echo=FALSE}
QRP1_Rank <- d50[[1]] %>% 
  select(Rank, QRP_1) %>% 
  group_by(Rank) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") 
Fals_Rank <- d50[[1]] %>% 
  group_by(Rank) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") 
Fabr_Rank <- d50[[1]] %>% 
  group_by(Rank) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") 
FF_Rank <- d50[[1]] %>% 
  group_by(Rank) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% round(2) %>% 
  mutate(Indicator = "FF") 

prev.Rank <- rbind(QRP1_Rank, Fals_Rank, Fabr_Rank, FF_Rank)[, c(4, 1, 2, 3)]
colnames(prev.Rank)[2:4] <- names(Means)[6:8]
```

```{r}
prevalence <- merge(prev.Field, prev.Rank, by.x = "Indicator")
cbind(prevalence, prev.overall) %>% 
  datatable()
cbind(prevalence, prev.overall)
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT