---
title: "Table 2"
author: "Gerko Vink"
date: Mean score and prevalence^^  of Questionable Research Practices (QRP), Falsification, and Fabrication stratified by Disciplinary Field and Academic Rank
output:
  word_document:
    toc: yes
    toc_depth: '5'
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: no
always_allow_html: true
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>


---

# Packages used
For this document we use the following packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(mice)     # Data imputation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(haven)    # Import data
library(DT)       # Interactive tables
library(ggplot2)  # Plotting device
library(reshape2) # Data shaping
library(labelled) # Advanced labelling
library(psych)    # Descriptive tables
library(tibble)   # Tibbles
library(RRreg)    # Randomized Response
```

---

# Load the data
```{r}
load(file = "../Workspaces/5. Preparation Imputed Datasets.Rdata")
options(DT.options = list(pageLength = 50)) # table options
```

```{r echo = FALSE}
## RR functions
RR2 <- function(df){
  df <- na.omit(df)
  y  <- df$Freq
  n  <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  Q <- P %x% P
  phat <- solve(Q) %*% pobs
  varp <- (n - 1)^-1 * solve(Q) %*% (diag(pobs) -  pobs %*% t(pobs)) %*% t(solve(Q))
  min95 <- phat - 1.96*sqrt(diag(varp))
  max95 <- phat + 1.96*sqrt(diag(varp))
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat, 3), paste("(", round(min95, 3), ",", round(max95, 3), ")", sep = "")))
}

RR1 <- function(df){
  y <- df$Freq
  n <- sum(y)
  pobs <- y / n
  P <- matrix(c(5, 1, 1, 5) / 6, 2, 2)
  phat <- solve(P) %*% pobs
  varp <- prod(pobs)/(n*(P[2,2]-P[2,1])^2)
  min95 <- phat - 1.96*sqrt(varp)
  max95 <- phat + 1.96*sqrt(varp)
  data.frame(df, phat = phat, lwr = min95, upr = max95, p.ci = paste(round(phat, 3), paste("(", round(min95, 3), ",", round(max95, 3), ")", sep = "")))
}
```

---

# Means
```{r echo = FALSE}
Overall <- d50[[1]] %>% 
  select(contains("Q")) %>% # select relevant columns
  select(!contains("_")) %>% # exclude raw
  melt(variable.name = "Practices") %>% 
  group_by(Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 2), ",", round(upr, 2), ")", sep = ""),
         mean = round(mean, 3),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, mean, ci, m.ci) 
mci.overall <- Overall %>% select(Practices, m.ci) %>% rename(Overall = m.ci)
```
```{r echo = FALSE}
Field <- d50[[1]] %>% 
  select(contains("Q"), Field) %>% # select relevant columns
  select(!contains("_"), Field) %>% # exclude raw
  melt(id.vars = "Field", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Field, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 2), ",", round(upr, 2), ")", sep = ""),
         mean = round(mean, 3),
         m.ci = paste(mean, ci, sep = " ")) %>% 
  select(Practices, Field, mean, ci, m.ci) 

mci.Field <- Field %>% dcast(Practices ~ Field, value.var = "m.ci") %>% .[, c(1, 5, 2, 4, 3)]
```

```{r echo = FALSE}
Rank <- d50[[1]] %>% 
  select(contains("Q"), Rank) %>% # select relevant columns
  select(!contains("_"), Rank) %>% # exclude raw
  melt(id.vars = "Rank", variable.name = "Practices", value.name = "Response") %>% 
  group_by(Rank, Practices) %>% 
  summarise_all(list(n = length, mean = mean, sd = sd)) %>% 
  mutate(lwr = mean - qnorm(.975) * (sd/sqrt(n)),
         upr = mean + qnorm(.975) * (sd/sqrt(n)),
         ci = paste("(", round(lwr, 2), ",", round(upr, 2), ")", sep = ""),
         mean = round(mean, 3)) %>% 
  select(Practices, Rank, mean, ci) 

mci.Rank <- Rank %>% mutate(m.ci = paste(mean, ci, sep = " ")) %>% dcast(Practices ~ Rank, value.var = "m.ci")
```

```{r echo = FALSE}
Means <- merge(mci.Field, mci.Rank, by.x = "Practices")
Means <- merge(Means, mci.overall, by.x = "Practices")

datatable(Means)
Means
```

---

# Prevalence
```{r echo = FALSE}
p.test <- function(x){
  t <- suppressWarnings(prop.test(x))
  paste(round(t$estimate, 3),
        paste("(", round(t$conf.int[1], 3), ",", round(t$conf.int[2], 3), ")", sep = ""))
}
QRP1_overall <- d50[[1]] %$% #RRP has no missings -so use 1st imputed set
  table(1 - QRP_1) %>% prop.table() %>% p.test
Fals_overall <- d50[[1]] %$% 
  table(RRfals) %>% 
  melt(value.name = "Freq") %>% 
  RR1() %>%  .$p.ci %>% .[2]
Fabr_overall <- d50[[1]] %$% 
  table(RRfabr) %>% 
  melt(value.name = "Freq") %>% 
  RR1() %>%  .$p.ci %>% .[2]
FF_overall <- d50[[1]] %$% 
  table(RRfals, RRfabr) %>% 
  melt(value.name = "Freq") %>% 
  RR2() %>% .$phat %>% .[2:4] %>% sum 

prev.overall <- data.frame(Overall = c(QRP1_overall, Fals_overall, Fabr_overall, round(FF_overall, 3)))
```
```{r echo=FALSE}
QRP1_Field <- d50[[1]] %>% 
  select(Field, QRP_1) %>% 
  group_by(Field) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") %>% 
  .[, c(5, 4, 1, 3, 2)] #reorder, cf. table
Fals_Field <- d50[[1]] %>% 
  group_by(Field) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") %>% 
  .[, c(5, 4, 1, 3, 2)] #reorder, cf. table
Fabr_Field <- d50[[1]] %>% 
  group_by(Field) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") %>% 
  .[, c(5, 4, 1, 3, 2)] #reorder, cf. table
FF_Field <- d50[[1]] %>% 
  group_by(Field) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "FF") %>% 
  .[, c(5, 4, 1, 3, 2)] #reorder, cf. table

prev.Field <- rbind(QRP1_Field, Fals_Field, Fabr_Field, FF_Field)
colnames(prev.Field)[2:5] <- names(Means)[2:5]
```
```{r echo=FALSE}
QRP1_Rank <- d50[[1]] %>% 
  select(Rank, QRP_1) %>% 
  group_by(Rank) %>% 
  group_map(~ sapply(., table, simplify = TRUE)) %>% 
  map(~.x %>% .[c(2, 1)] %>% t() %>% p.test) %>% 
  do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "ANY_QRP") 
Fals_Rank <- d50[[1]] %>% 
  group_by(Rank) %>% 
  group_map(~.x %$% 
              table(RRfals) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Falsification") 
Fabr_Rank <- d50[[1]] %>% 
  group_by(Rank) %>% 
  group_map(~.x %$% 
              table(RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR1() %>%  .$p.ci %>% .[2]) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% 
  mutate(Indicator = "Fabrication") 
FF_Rank <- d50[[1]] %>% 
  group_by(Rank) %>% 
  group_map(~.x %$% 
              table(RRfals, RRfabr) %>% 
              melt(value.name = "Freq")) %>% 
              map(~.x %>% RR2() %>%  .$phat %>% .[2:4] %>% sum) %>% 
   do.call(rbind, .) %>% t() %>% as.data.frame() %>% round(3) %>% 
  mutate(Indicator = "FF") 

prev.Rank <- rbind(QRP1_Rank, Fals_Rank, Fabr_Rank, FF_Rank)[, c(4, 1, 2, 3)]
colnames(prev.Rank)[2:4] <- names(Means)[6:8]
```

```{r}
prevalence <- merge(prev.Field, prev.Rank, by.x = "Indicator")
cbind(prevalence, prev.overall) %>% 
  datatable()
cbind(prevalence, prev.overall)
```

---

# Session Info
```{r}
sessionInfo()
```

---

# Document info
Signed: 
[Gerko Vink](https://www.gerkovink.com), 

```{r}
timestamp()
```

---

END of DOCUMENT